### 2014-03-04 paper/paper.tex
initialized the latex paper

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{EasyMerge - Clone Code Refactor}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Shengying Pan\\
       \affaddr{University of Waterloo}\\
       \email{s5pan@uwaterloo.ca}
% 2nd. author
\alignauthor
Haocheng Qin\\
       \affaddr{University of Waterloo}\\
       \email{h7qin@uwaterloo.ca}
% 3rd. author
\alignauthor Yahui Chen\\
       \affaddr{University of Waterloo}\\
       \email{y556chen@uwaterloo.ca}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}

\section{Clone Code Detection}

\section{Clone Merging Algorithm}

\section{Experimental Results}

\section{Conclusions}

\section{Future Work}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
\balancecolumns
% That's all folks!
\end{document}

### 2014-03-04 EasyMerge/main.py
initilize

@@ -1,0 +1,19 @@
+'''
+Created on Mar 4, 2014
+
+@author: Shengying
+'''
+
+import sys
+from PyQt4 import QtGui
+
+if __name__ == '__main__':
+    app = QtGui.QApplication(sys.argv)
+
+    w = QtGui.QWidget()
+    w.resize(250, 150)
+    w.move(300, 300)
+    w.setWindowTitle('Simple')
+    w.show()
+    
+    sys.exit(app.exec_())

### 2014-03-05 paper/paper.tex
wrote some introduction

@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms to
-the formatting guidelines for ACM SIG Proceedings.
-It complements the document \textit{Author's Guide to Preparing
-ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file.
+Abstract goes here.
 \end{abstract}
@@
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
@@
 \section{Introduction}
+In software development, it's very common seeing developers reuse code fragments by copying and pasting with or without minor adaptation.
+Moreover, for large scale projects, developers are often too lazy to browse existing source files so that they may rewrite similar or even identical functions which
+were already in the code base. As a result, software systems often contain sections of code that are very similar, called code clones.
+
+Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
+in code bases are unnecessary duplications. By detecting, categorizing,
+and removing code clones, we can produce easier to understand, cleaner, and more reusable code.
+
+Clone detection has been an avid research topic in the field of software engineering for decades. Fortunately, several automated techniques for detecting code clones
+have already been proposed.
+
+\section{Background}
 
@@
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file
@@
 %\balancecolumns
-\appendix
+%\appendix
 %Appendix A
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-\balancecolumns
+%\subsection{References}
+%Generated by bibtex from your ~.bib file.  Run latex,
+%then bibtex, then latex twice (to resolve references)
+%to create the ~.bbl file.  Insert that ~.bbl file into
+%the .tex source file and comment out
+%the command \texttt{{\char'134}thebibliography}.
+%\balancecolumns
 % That's all folks!

### 2014-03-06 paper/paper.tex
added something to introduction

@@
 Clone detection has been an avid research topic in the field of software engineering for decades. Fortunately, several automated techniques for detecting code clones
-have already been proposed.
+have already been proposed. However, how to deal with detected clones, e.g. how to distinguish necessary clones from unnecessary ones and how to refactor code to remove
+unnecessary clones still remain a big problem in not only commercial but also academic domain. As a result, in this paper, we try to classify code clones and build
+a recommendation system called EasyMerge to help developers merge unnecessary clones on top of current state-of-the-art clone detection approach.
 

### 2014-03-06 paper/paper.tex
made some changes

@@
 
-\terms{Theory}
+\terms{Software Engineering, Recommendation System}
 
-\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings
+\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System} % NOT required for Proceedings
 
@@
 Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
-in code bases are unnecessary duplications. By detecting, categorizing,
+in code bases are unnecessary duplications. 
+Code duplication can be a significant drawback, leading to bad design, and increased probability of bug occurrence and propagation. As a result, it can significantly
+increase maintenance cost, and form a barrier for software evolution. By detecting, categorizing,
 and removing code clones, we can produce easier to understand, cleaner, and more reusable code.
@@
 a recommendation system called EasyMerge to help developers merge unnecessary clones on top of current state-of-the-art clone detection approach.
+
+More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detection approach, for its overall performance, coverage of multiple clone types, and availability.
+EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding or development.
 

### 2014-03-07 paper/paper.tex
write more to paper

--- 2014-03-06 paper/paper.tex
@@
 
-\title{EasyMerge - Clone Code Refactor}
+\title{EasyMerge - A New Tool for Code Clones Refactoring}
 %
@@
 Shengying Pan\\
+       \affaddr{School of Computer Science}\\
        \affaddr{University of Waterloo}\\
@@
 Haocheng Qin\\
+       \affaddr{School of Computer Science}\\
        \affaddr{University of Waterloo}\\
@@
 \alignauthor Yahui Chen\\
+       \affaddr{School of Computer Science}\\
        \affaddr{University of Waterloo}\\
@@
 
+More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detection approach. CloneDigger is one of the best available 
+clone detection tools currently for its overall performance, coverage of multiple clone types, and availability. 
+EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding and development.
+
+The paper is structured as following: we first go through the basics, background, and current state of clone detection and code clone refactoring in general.
+Then we introduce and discuss the fundamentals of CloneDigger and the anti-unification algorithm it is using to detect clones. Afterwards, we explain EasyMerge's
+work flow and underlying techniques. And at the end, we set up testing environment and discuss the experimental results of running EasyMerge against several
+open source projects of different scales.
+
 \section{Background}
@@
 
-\section{Clone Merging Algorithm}
+\section{EasyMerge}
 

### 2014-03-09 paper/paper.tex
fixing references

@@
 
-Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
+Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy1}. Many code clones
 in code bases are unnecessary duplications. 
@@
 \section{Background}
+Roy and Cordy has done a great work \cite{roy2}
 

### 2014-03-09 paper/paper.tex
started writing background section in the paper

@@
 \documentclass{acm_proc_article-sp}
+
+\newdef{definition}{Definition}
 
@@
 
-The paper is structured as following: we first go through the basics, background, and current state of clone detection and code clone refactoring in general.
+The rest of the paper is structured as follows: we first go through the basics, background, and current state of clone detection and code clone refactoring in general.
 Then we introduce and discuss the fundamentals of CloneDigger and the anti-unification algorithm it is using to detect clones. Afterwards, we explain EasyMerge's
@@
 \section{Background}
-Roy and Cordy has done a great work \cite{roy2}
+Roy, Cordy, and Koschke have done a great work \cite{roy2} writing an overview paper explaining the basics of clone detection, and providing a complete comparison of essential
+strengths and weaknesses of both individual tools and techniques and alternative approaches in general. It gives us all the needed preliminaries to focus on clone refactoring rather
+than spending time working on the detection part. We begin with a basic introduction to clone detection terminology in Roy's paper.
+
+\begin{definition}
+(Code Fragment). A code fragment (CF) is any sequence of code lines (with or without comments). It can be of any granularity, e.g., function
+definition, begin-end block, or sequence of statements. A $CF$ is identified by its file name and begin-end line numbers in the original code base
+and is denoted as a triple ($CF.FileName$, $CF.BeginLine$, $CF.EndLine$).
+\end{definition}
+
+\begin{definition}
+(Code Clone). A code fragment $CF2$ is a clone of another code fragment $CF1$ if they are similar by some given definition of similarity, that is, 
+$f(CF1) = f(CF2)$ where $f$ is the similarity function (see clone types below). Two fragments that are similar to each other form a clone pair
+$(CF1, CF2)$, and when many fragments are similar, they form a clone class or clone group.
+\end{definition}
+
+\begin{definition}
+(Clone Types). There are two main kinds of similarity between code fragments. Fragments can be similar based on the similarity of their program text,
+or they can be similar based on their functionality (independent of their text). The first kind of clone is often the result of copying a code fragment and
+pasting into another location. In the following we provide the types of clones based on both the textual (Type 1 to 3)\cite{bellon} and functional (Type 4)\cite{gabel, komondoor} similarities:
+
+\begin{itemize}
+\item {\bf Type-1:} Identical code fragments except for variations in whitespace, layout and comments.
+\item {\bf Type-2:} Syntactically identical fragments except for variations in identifiers, literals, types, whitespace, layout and comments.
+\item {\bf Type-3:} Copied fragments with further modifications such as changed, added or removed statements, in addition to variations in identifiers, literals, types, whitespace, layout and comments.
+\item {\bf Type-4:} Two or more code fragments that perform the same computation but are implemented by different syntactic variants.
+\end{itemize}
+\end{definition}
 

### 2014-03-09 paper/paper.tex
added abstract section to the paper

@@
 \begin{abstract}
-Abstract goes here.
+Code clones are common in medium to large scale software projects. Oftentimes, unnecessary clones cause troubles to code base maintenance and code reusability. 
+Over past decades, many techniques and approaches have been proposed to detect code clones. However, how to refactor clones is still a challenging topic to software
+engineers. Even text-wise identical code clones can be semantically different when they are referring variables and calling functions outside. And the problem is more 
+complex when scopes and dependencies are considered. Furthermore, not all clones can be refactored as they may be part of tests or needed to maintain dependencies across multiple
+libraries. As a result, we need adaptive clone refactoring tools that can locate unnecessary clones and alert possible implications in the procedure to help
+software engineers be more efficient and make less mistakes in the refactoring process.
+
+In this paper, we introduce EasyMerge, a new tool to refactor code clones.
 \end{abstract}

### 2014-03-10 paper/paper.tex
added a test case

@@
 Code clones are common in medium to large scale software projects. Oftentimes, unnecessary clones cause troubles to code base maintenance and code reusability. 
-Over past decades, many techniques and approaches have been proposed to detect code clones. However, how to refactor clones is still a challenging topic to software
+Over past decades, many techniques and approaches have been proposed to detect code clones. However, how to refactor clones is still a very challenging topic to software
 engineers. Even text-wise identical code clones can be semantically different when they are referring variables and calling functions outside. And the problem is more 
@@
 
-In this paper, we introduce EasyMerge, a new tool to refactor code clones.
+In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based clone detection algorithm
 \end{abstract}
@@
 
-\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System} % NOT required for Proceedings
+\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System, Python} % NOT required for Proceedings
 

### 2014-03-10 EasyMerge/tests/beets/mediafile.py

@@ -1,0 +1,1558 @@
+# This file is part of beets.
+# Copyright 2014, Adrian Sampson.
+#
+# Permission is hereby granted, free of charge, to any person obtaining
+# a copy of this software and associated documentation files (the
+# "Software"), to deal in the Software without restriction, including
+# without limitation the rights to use, copy, modify, merge, publish,
+# distribute, sublicense, and/or sell copies of the Software, and to
+# permit persons to whom the Software is furnished to do so, subject to
+# the following conditions:
+#
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+"""Handles low-level interfacing for files' tags. Wraps Mutagen to
+automatically detect file types and provide a unified interface for a
+useful subset of music files' tags.
+
+Usage:
+
+    >>> f = MediaFile('Lucy.mp3')
+    >>> f.title
+    u'Lucy in the Sky with Diamonds'
+    >>> f.artist = 'The Beatles'
+    >>> f.save()
+
+A field will always return a reasonable value of the correct type, even
+if no tag is present. If no value is available, the value will be false
+(e.g., zero or the empty string).
+"""
+import mutagen
+import mutagen.mp3
+import mutagen.oggopus
+import mutagen.oggvorbis
+import mutagen.mp4
+import mutagen.flac
+import mutagen.monkeysaudio
+import mutagen.asf
+import datetime
+import re
+import base64
+import math
+import struct
+import imghdr
+import os
+import logging
+import traceback
+from beets.util.enumeration import enum
+
+__all__ = ['UnreadableFileError', 'FileTypeError', 'MediaFile']
+
+
+
+# Logger.
+log = logging.getLogger('beets')
+
+
+
+# Exceptions.
+
+# Raised for any file MediaFile can't read.
+class UnreadableFileError(Exception):
+    pass
+
+# Raised for files that don't seem to have a type MediaFile supports.
+class FileTypeError(UnreadableFileError):
+    pass
+
+
+
+# Constants.
+
+# Human-readable type names.
+TYPES = {
+    'mp3':  'MP3',
+    'aac':  'AAC',
+    'alac':  'ALAC',
+    'ogg':  'OGG',
+    'opus': 'Opus',
+    'flac': 'FLAC',
+    'ape':  'APE',
+    'wv':   'WavPack',
+    'mpc':  'Musepack',
+    'asf':  'Windows Media',
+}
+
+
+
+# Utility.
+
+def _safe_cast(out_type, val):
[…]

### 2014-03-10 EasyMerge/clonedigger/html_report.py
f**k msg

@@ -24,6 +24,10 @@ import traceback
 import os.path
 from cgi import escape
 
+import debug
+
+import pickle
+
 import arguments
 import anti_unification
 import python_compiler
@@ -104,11 +108,12 @@ class HTMLReport(Report):
         for clone_i in range(len(self._clones)):
             try:
                 clone = self._clones[clone_i]
+                #debug.print_clone(clone)
                 s = '<P>'
                 s += '<B>Clone # %d</B><BR>'%(clone_i +1,)
 #           s = '<P> Clone detected in source files "%s" and "%s" <BR>\n' % (sequences[0].getSourceFile().getFileName(), sequences[1].getSourceFile().getFileName())
                 s+= 'Distance between two fragments = %d <BR>' %(clone.calcDistance())
-                s+= 'Clone size = ' + str(max([len(set(clone[i].getCoveredLineNumbers())) for i in [0,1]] ))
+                s+= 'Clone size = ' + str(([(set(clone[i].getCoveredLineNumbers())) for i in [0,1]] ))
                 s+= '<TABLE NOWRAP WIDTH=100% BORDER=1>'
                 s+= eclipse_start
                 s+= '<TR>'
@@ -231,7 +236,7 @@ class HTMLReport(Report):
                             print 'using diff highlight'
                             (d,u) = use_diff()
                     for j in [0,1]:                 
-                        t.append('<TD>\n' + d[j] + '</TD>\n')
+                        t.append('<TD>\n' + d[j] + "<BR>" + str(statements[j]) + '</TD>\n')
                     if u.getSize() > 0:
                         color = 'RED'
                     else:

### 2014-03-10 EasyMerge/clonedigger/python_compiler.py

@@ -36,7 +36,7 @@ class PythonCompilerSourceFile (SourceFile):
     extension = 'py'
     distance_threshold = 5
     size_threshold = 5
-    ignored_statements = ['Import', 'From']
+    ignored_statements = []#'Import', 'From']
     def __init__(self, file_name, func_prefixes = ()):
         SourceFile.__init__(self, file_name)
         self._func_prefixes = func_prefixes

### 2014-03-10 EasyMerge/testcase/self_written/a.py

@@ -1,0 +1,54 @@
+import os, sys
+import time as sy
+import re
+import t.b
+from b import T,T2
+
+
+print sy.time()
+class T:
+	class TT:
+		at = 5
+		def __init__(self):
+			self.bt = 6
+		def test(self):
+			print "t"
+	a = 0
+	def __init__(self):
+		self.b = 1
+		self.c = "c"
+		self.d = True
+	def test():
+		pass
+a = b.T()
+print a.aa
+def cc():
+	print "first"
+
+c = T.TT()
+d = T()
+e = TT()
+T.TT().test()
+
+for i in range(5):
+	print "qnmd"
+
+print c
+print str(c)
+
+cc()
+
+def b(c,i=2):
+	def cc():
+		print "cc here"
+	print cc()
+	print c
+	print str(c)
+	if c:	
+		return c
+	else:
+		return None
+print c.test()
+print B.c.test()
+cc()
+print 7

### 2014-03-10 EasyMerge/testcase/self_written/test.py

@@ -1,0 +1,11 @@
+class cA:
+	def a(self):
+		i = 0
+		def b():
+			print b.__class__
+			#print b.__name__
+		print b.__name__
+
+ca = cA()
+ca.a()
+print ca.a.__name__

### 2014-03-10 paper/paper.tex

@@
 
-In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based clone detection algorithm
+In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based anti-unification clone detection algorithm and 
+refactors software projects written in Python. It adds intelligence to code clone refactoring by categorizing clones and generating refactoring recommendations
+based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone segments in functions,
+classes, and across different scopes. It ensures functionality-wise consistency before and after refactoring and provide warnings when potential refactoring could lead to
+unwanted complexity or cause readability issues.
 \end{abstract}
@@
 
-\section{Clone Code Detection}
+\section{CloneDigger}
 
@@
 
-\section{Conclusions}
-
-\section{Future Work}
-
 %ACKNOWLEDGMENTS are optional
 \section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
 

### 2014-03-11 paper/paper.tex
updating paper

@@
 \section{Background}
+\subsection{Clone Detection}
 Roy, Cordy, and Koschke have done a great work \cite{roy2} writing an overview paper explaining the basics of clone detection, and providing a complete comparison of essential
@@
 \end{definition}
+
+There are many different techniques to detect code clones. In Roy's paper \cite{roy2}, they covered tools of textual approaches, lexical approaches, syntactic approaches,
+semantic approaches and hybrids. Different tools have advantages and disadvantages for different facets (usage, interaction, language, clone information, technical aspect, 
+adjustment, processing, and evaluation) and behave quite differently for some scenarios. As clone detection is still an on-going research, it's hard to say one tool is the best
+at the moment. However, for the purpose of building EasyMerge, we want to pick a tool that is cross-platform, freely available, efficient, covering multiple clone types, and can
+handle different editing scenarios decently. Thus we chose CloneDigger \cite{bulychev} after a comprehensive comparison.
+
+\subsection{Clone Refactoring}
+On the other hand, for clone refactoring, most proposed solutions use some pre-defined metrics as the refactoring guidance to help users determine whether the 
+code clones are suitable for refactoring. For example, Balazinska \cite{balazinska} proposed to use 21 metrics to measure the suitability for refactoring. Higo \cite{higo}
+developed ARIES tools, using the code detection tool CCFinder and environment analysis tool Gemini to find the clones can be refactored. And Schulze \cite{schulze}
+proposed a new metric DIST (distance of the code clones). Unlike them, instead of calculating distance between code segments and only merging close clones, EasyMerge 
+try to fix the differences and merge as many clones as possible without introducing extra complexity.
+
+For the actual merging process, currently existing research mainly focus on using refactoring patterns \cite{fowler}, especially ``Extract Method" and ``Pull Up Method".
+"Extract Method" means that a fragment of source code is extracted and redefined as a new method. ``Pull Up Method" means that the same methods defined in child
+classes are pulled up to its parent class. In general, they are both merging similar code blocks into one newly created function, and ``Pull Up Method" only differs from 
+``Extract Method" as it places the newly created function into the super class when code blocks are inside functions sharing the same parent class.
+
+Unfortunately, code clones may be coupled with surrounding code, its inheritance tree, or other independent classes/code blocks. For instance:
 

### 2014-03-14 paper/paper.tex
added CloneDigger to paper

@@
 \newdef{definition}{Definition}
+
+\makeatletter
+\newif\if@restonecol
+\makeatother
+\let\algorithm\relax
+\let\endalgorithm\relax
+\usepackage[ruled,vlined]{algorithm2e}
+
+\usepackage{enumerate}
 
@@
 refactors software projects written in Python. It adds intelligence to code clone refactoring by categorizing clones and generating refactoring recommendations
-based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone segments in functions,
+based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone fragments in functions,
 classes, and across different scopes. It ensures functionality-wise consistency before and after refactoring and provide warnings when potential refactoring could lead to
@@
 developed ARIES tools, using the code detection tool CCFinder and environment analysis tool Gemini to find the clones can be refactored. And Schulze \cite{schulze}
-proposed a new metric DIST (distance of the code clones). Unlike them, instead of calculating distance between code segments and only merging close clones, EasyMerge 
+proposed a new metric DIST (distance of the code clones). Unlike them, instead of calculating distance between code fragments and only merging close clones, EasyMerge 
 try to fix the differences and merge as many clones as possible without introducing extra complexity.
@@
 
-Unfortunately, code clones may be coupled with surrounding code, its inheritance tree, or other independent classes/code blocks. For instance:
+Unfortunately, code clones may be coupled with surrounding code, its inheritance tree, or other independent classes/code blocks. For instance, code fragments inside clone pairs
+may contain function calls or variable references which are not defined inside the fragments. Furthermore, functions and variables of the same names may be in fact different
+at different locations of the code base. For example, if we have a code clone fragment as following:
+
+\IncMargin{1em}
+\begin{algorithm}
+	for x in range(0, 3):
+
+		\Indp a = x + 1
+
+		b = f(x)
+
+		c = d + x
+\end{algorithm}
+\DecMargin{1em}
+
+We are calling function {\bf f()} where the definition of {\bf f()} can be different from fragment to fragment. Moreover, the value of variable {\bf d} is potentially different, too.
+The current approach to solve this problem is to pass such external functions and variables as parameters to newly generated methods from the ``Extract Method" refactoring pattern.
+For instance:
+
+\IncMargin{1em}
+\begin{algorithm}
+	def helper(p1, p2):
+
+		\Indp for x in range(0, 3):
+
+			\Indp a = x + 1
+
+			b = p1(x)
+
+			c = p2 + x
+
+		\Indm \Indm helper(f, d)
+
+\end{algorithm}
+\DecMargin{1em}
+
+However, this creates two new problems. Firstly, in this example, the scope of b was changed. It is now inside the helper function and no longer available to code after the clone fragment
+which could potentially cause reference errors. Secondly, when the length of the clone fragment is too long, we could possibly end up with a helper function of tons of parameters
+which in turn make the code after refactoring harder to understand and is against our goal to improve readability. And the most intuitive approach to solve the first problem
+is to return b and such variables from the ``Extracted Method" which introduces even more complexity.
+
+As a result, for recently proposed refactoring approach \cite{li} and the tools mentioned at the beginning of this subsection, they count the number of such external references
+in a code clone fragment as the key factor of their refactoring guideline metrics. 
+And clone fragments of too many such occurrences will not be recommended for refactoring.
+Furthermore, in Li's work \cite{li}, after standardization, it can also be used to refactor semantical
+similar but syntax-wise different clones by moving different function references to extracted method's parameters.
+
+Unlike most of current clone refactoring approaches that use token-based CCFinder \cite{kamiya} for clone detection, EasyMerge uses a newer detection tool called CloneDigger.
+Compared to CCFinder, CloneDigger is cross-platform and freely available as an open source project. Moreover, based on evaluation from Roy \cite{roy2},
+CloneDigger performs no worse than CCFinder in all detection scenarios and is actually better in certain scenarios e.g. a programmer copies a function that calculates the sum
+and product of a loop variable and calls another function, foo() with these values as parameters three times, making changes in whitespace in the first fragment (S1(a)), changes
+in commenting in the second (S1(b)), and changes in formatting in the third (S1(c)). In the following section, we will go over the basic ideas behind CloneDigger and its anti-unification
+algorithm.
 
 \section{CloneDigger}
+\subsection{Overview}
+Techniques for detecting duplicate code can be classified according to several criteria.
+Code can be viewed as similar based on syntactic criteria or at a semantic level.
+CloneDigger considers only syntactic similarity.
+The algorithm is approached based on abstract syntax trees.
+The algorithm of finding duplicates consists of several phases.
+In the beginning all statements are partitioned into clusters using anti-unification distance and the code is abstractly viewed as sequence of cluster identifiers.
+All pairs of identical sequences of cluster IDs, which have similar statements in corresponding positions, are globally checked for similarity using anti-unification distance.
+
+\subsection{Preliminaries}
+Anti-unification is a general expression of two given terms.
+Let $E_{1}$ and $E_{2}$ be two terms.
+Anti-unification E is a generalization of $E_{1}$ and $E_{2}$ if there exist two substitutions $\sigma_{1}$ and $\sigma_{2}$ such that $\sigma_{1}(E)=E_{1}$ and $\sigma_{2}(E)=E_{2}$.
+The most specific generalization of $E_{1}$ and $E_{2}$.
+The most specific generalization of $E_{1}$ and $E_{2}$ is called anti-unifier.
+The anti-unifier tree of two trees $T_{1}$ and $T_{2}$ is obtained by replacing some subtrees in $T_{1}$ and $T_{2}$ by special nodes.m containing term placeholders which are marked with integers, such as $?_{n}$.
+An anti-unifier stores only the common top-level tree structure and therefore details may be ignored.
+
+The anti-unification distance is defined as follows: let U be the anti-unifier of two trees $T_{1}$ and $T_{2}$ with substitutions $\sigma_{1}$ and $\sigma_{2}$.
+$\sigma_{1}$ and $\sigma_{2}$ are mappings from the set \{$?_{1}$, $?_{2}$, ..., $?_{n}$\} to substituting trees.
+Anti-unification distance between $T_{1}$ and $T_{2}$ as a sum of sizes of substituting trees in $\sigma_{1}$ and $\sigma_{2}$.
+The distance doesn't allow the permutation of siblings or changing the number of child nodes.
+
+\subsection{Duplicate Code Detection Algorithm}
+The method of finding duplicate code consists of three phases:
+\begin{enumerate}[step 1]
+
+    \item Partitioning similar statements into clusters
+
+    Identify similar statements using anti-unification and partition them into clusters.
+A two-pass clustering algorithm is used.
+The first pass of the algorithm compare each new statement with the anti-unifiers of all existing clusters.
+The function $add\_cost$ is used to compute the cost of adding a tree $T$ to the cluster consisting of $n$ trees with anti-unifier $au$.
+Let $au'$ be the result of anti-unification of $T$ and $au$ with substitutions $\sigma_{1}$ and $\sigma_{2}$: $\sigma_{1}(au') = au$, $\sigma_{2}(au') = T$.
+$add\_cost$ is defined as $n \times |\sigma_{1}| + |\sigma_{2}|$.
+During the second pass all the statements re traversed again and for each statement we search for the most similar pattern from the set produced in the previous pass using the anti-unification distance.
+After the first phase each statement is marked with its cluster ID, two statements with the same cluster ID are considered similar in this preliminary view.
+
+    \item Finding pairs of identical cluster sequences
+    All pairs of sequences of statements, which are large enough, are identically labeled.
+
+    \item Examining code sequences for overall similarity
+    All candidates are checked as a whole using anti-unification distance. The occurrences of the same variable refers to one leaf in the abstract syntax tree increase the quality of the algorithm.
+\end{enumerate}
+
+Now we can move on to introduce EasyMerge and how it works behind the scene.
 
@@
 %ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
+%\section{Acknowledgements}
 

### 2014-03-14 EasyMerge/main.py
started working on UI;

@@ -5,15 +5,12 @@ Created on Mar 4, 2014
 '''
 
 import sys
+from ui.background import Background
 from PyQt4 import QtGui
 
 if __name__ == '__main__':
     app = QtGui.QApplication(sys.argv)
-
-    w = QtGui.QWidget()
-    w.resize(250, 150)
-    w.move(300, 300)
-    w.setWindowTitle('Simple')
-    w.show()
-    
+    bg = Background()
+    bg.setWindowTitle('EasyMerge - Clone Merger')
+    bg.showMaximized()
     sys.exit(app.exec_())

### 2014-03-14 EasyMerge/ui/background.py

@@ -1,0 +1,23 @@
+from PyQt4 import QtGui
+
+class Background(QtGui.QWidget):
+    def __init__(self):
+        super(Background, self).__init__()
+        self._list = QtGui.QListWidget(self)
+        self._tabs = QtGui.QTabWidget(self)
+        self._result = QtGui.QTextBrowser(self)
+        self._merge = QtGui.QPushButton('Merge', self)
+        self.initUI()
+
+    def initUI(self):
+        grid = QtGui.QGridLayout()
+        grid.addWidget(self._list, 0, 0, 2, 1)
+        grid.addWidget(self._tabs, 0, 1, 1, 1)
+        grid.addWidget(self._result, 1, 1, 2, 1)
+        grid.addWidget(self._merge, 2, 0, 1, 1)
+
+        grid.setColumnStretch(0, 1)
+        grid.setColumnStretch(1, 3)
+
+        self.setLayout(grid)
+

### 2014-03-14 EasyMerge/ui/background.py
ui

@@ -7,14 +7,20 @@ class Background(QtGui.QWidget):
         self._tabs = QtGui.QTabWidget(self)
         self._result = QtGui.QTextBrowser(self)
         self._merge = QtGui.QPushButton('Merge', self)
+        self._analyze = QtGui.QPushButton('Analyze', self)
+        self._open = QtGui.QPushButton('Open Source', self)
+        self._source = QtGui.QLineEdit(self)
         self.initUI()
 
     def initUI(self):
         grid = QtGui.QGridLayout()
-        grid.addWidget(self._list, 0, 0, 2, 1)
-        grid.addWidget(self._tabs, 0, 1, 1, 1)
-        grid.addWidget(self._result, 1, 1, 2, 1)
-        grid.addWidget(self._merge, 2, 0, 1, 1)
+        grid.addWidget(self._open, 0, 0, 1, 1)
+        grid.addWidget(self._source, 0, 1, 1, 1)
+        grid.addWidget(self._analyze, 0, 2, 1, 1)
+        grid.addWidget(self._list, 1, 0, 2, 1)
+        grid.addWidget(self._tabs, 1, 1, 1, 2)
+        grid.addWidget(self._result, 2, 1, 2, 2)
+        grid.addWidget(self._merge, 3, 0, 1, 1)
 
         grid.setColumnStretch(0, 1)
         grid.setColumnStretch(1, 3)

### 2014-03-14 EasyMerge/merger/SimpleStmtMerge.py
Thursday

@@ -6,6 +6,9 @@ Created on Mar 12, 2014
 from optparse import OptionParser
 import clonedigger.clonedigger as digger
 import clonedigger.anti_unification as anti_unification
+from clonedigger.abstract_syntax_tree import StatementSequence
+
+import test
 
 def sortDuplicates(duplicates):
     def f(a,b):
@@ -97,14 +100,15 @@ Don't forget to remove automatically generated sources, tests and third party li
 Notice:
 The semantics of threshold options is discussed in the paper "Duplicate code detection using anti-unification", which can be downloaded from the site http://clonedigger.sourceforge.net . All arguments are optional. Supported options are: 
 """)
-    orig_duplicates = digger.main(cmdline)
+    (src_ast_list, orig_duplicates) = digger.main(cmdline)
     sortDuplicates(orig_duplicates)
     duplicate_set = mergeStmtSeqs(orig_duplicates) 
     removeOverlappedSeqs(duplicate_set)
-    return duplicate_set
+    return (src_ast_list,duplicate_set)
 
 
 def checkSeqType(seq):
+    threshold = 4
     type = "Unknown"
     type_set = []
     for i in range(len(seq)):
@@ -115,33 +119,57 @@ def checkSeqType(seq):
                 type = "Def"
             else:
                 type = "Stmt"
-            type_set.append((0,type))
+            type_set.append(([0],type,len(i.getSourceLines())))
         else:
             if i.getName()=="Function":
                 type = "Def"
             else:
                 type = "Stmt"
             if type!=type_set[-1][1]:
-                type_set.append((id, type))
+                type_set.append(([id], type,len(i.getSourceLines())))
             else:
-                type_set[-1]=(id,type)
+                li = list(type_set[-1][0])
+                li.append(id)
+                type_set[-1]=(li,type,type_set[-1][2]+len(i.getSourceLines()))
     if len(type_set)==1:
         return type_set[0][1]
     else:
-        return type_set
+        new_set = []
+        for i in type_set:
+            if i[2]>=threshold:
+                new_seq = []
+                for j in i[0]:
+                    new_seq.append(seq[j])
+                new_set.append(new_seq)
+        return ("Mix",new_set)
 
-def checkSetType(cluster):
-    type = "Unknown"
-    for seq in cluster:
-        cur_type = checkSeqType(seq)
-        if type!="Unknown" and type!=cur_type:
[…]

### 2014-03-14 EasyMerge/merger/clonedigger/clonedigger.py

@@ -131,6 +131,8 @@ def main(cmdline):
         arguments.size_threshold = supplier.size_threshold
     
     report.startTimer('Construction of AST')
+    
+    src_ast_list = {}
 
     def parse_file(file_name, func_prefixes):
         try:
@@ -145,7 +147,7 @@ def main(cmdline):
             source_file.getTree().propagateCoveredLineNumbers()
             source_file.getTree().propagateHeight()
             source_files.append(source_file)
-            #debug.AST(source_file.getTree()).output(file_name+".out")
+            src_ast_list[file_name] = debug.AST(source_file.getTree())
             report.addFileName(file_name)                
             print 'done'
         except:
@@ -193,6 +195,7 @@ def main(cmdline):
             
     
     try:
+        print "Writting Report"
         report.writeReport(output_file_name)
     except:
         print "catched error, removing output file"
@@ -201,11 +204,9 @@ def main(cmdline):
         raise 
     
     
-    return duplicates   
+    return (src_ast_list, duplicates)   
         
-    report.sortByCloneSize()
-    
-     
+  
         
     '''for s in duplicate_set:
         print duplicate_set.index(s),":", tagging(s[0])[2]-tagging(s[0])[1]

### 2014-03-14 EasyMerge/merger/clonedigger/debug.py

@@ -44,7 +44,7 @@ class AST:
             scope_result.append(scope)
         if tree.getName()=="CallFunc" and not in_call:
             in_call = True
-            call_result.append((tree.getLineNumbers()[0], self.parse_call(tree.getChilds()[0]), scope))
+            call_result.append((tree,(tree.getLineNumbers()[0], self.parse_call(tree.getChilds()[0]), scope)))
         for i in tree.getChilds():
             new_scope = list(scope)            
             self.parse_tree(i, scope, scope_result, call_result, in_call)
@@ -63,8 +63,8 @@ class AST:
             elif call.getChilds()[0].getName()=="Subscript" or call.getChilds()[0].getName()=="Slice":
                 return [str(call.getChilds()[0]),call.getChilds()[1].getName()[1:-1]]
             else:
-                print "Exception Here", call.getChilds()[0].getName()
-        print "Exception Here", call.getName()
+                return [call.getChilds()[0].getName()+":"+str(call.getChilds()[0])]+[call.getChilds()[1].getName()[1:-1]]              
+        return [call.getName()+":"+str(call)]+[call.getChilds()[0].getName()[1:-1]] 
     
     
     def process_imports(self):
@@ -73,7 +73,7 @@ class AST:
             if i[0].find(".")<0:
                 new_i = [self.imports.index(i), i[0]]
             else:
-                new_i = [new_i[0]]+i[0].split('.')
+                new_i = [self.imports.index(i), i[0].split('.')]
             new_imports.append(new_i)
             if i[1]!=None:
                 if i[1].find(".")<0:
@@ -96,7 +96,9 @@ class AST:
         build_in_name = ["abs", "divmod", "input", "open", "staticmethod", "all", "enumerate", "int", "ord", "str", "any", "eval", "isinstance", "pow", "sum", "basestring", "execfile", "issubclass", "print", "super", "bin", "file", "iter", "property", "tuple", "bool", "filter", "len", "range", "type", "bytearray", "float", "list", "raw_input", "unichr", "callable", "format", "locals", "reduce", "unicode", "chr", "frozenset", "long", "reload", "vars", "classmethod", "getattr", "map", "repr", "xrange", "cmp", "globals", "max", "reversed", "zip", "compile", "hasattr", "memoryview", "round", "__import__", "complex", "hash", "min", "set", "apply", "delattr", "help", "next", "setattr", "buffer", "dict", "hex", "object", "slice", "coerce", "dir", "id", "oct", "sorted", "intern"]
[…]

### 2014-03-14 EasyMerge/merger/helper.py

@@ -1,0 +1,12 @@
+if val is None:
+    return 0.0
+elif isinstance(val, int) or isinstance(val, float):
+    return float(val)
+else:
+    if not isinstance(val, basestring):
+        val = unicode(val)
+    val = re.match(r'[\+-]?[0-9\.]*', val.strip()).group(0)
+    if not val:
+        return 0.0
+    else:
+        return float(val)

### 2014-03-14 EasyMerge/merger/helper2.py

@@ -1,0 +1,12 @@
+if val is None:
+    return 0
+elif isinstance(val, int) or isinstance(val, float):
+    return int(val)
+else:
+    if not isinstance(val, basestring):
+        val = unicode(val)
+    val = re.match(r'[\+-]?[0-9\.]*', val.strip()).group(0)
+    if not val:
+        return 0
+    else:
+        return int(val)

### 2014-03-14 EasyMerge/merger/test.py

@@ -1,0 +1,26 @@
+'''
+Created on Mar 14, 2014
+
+@author: h7qin
+'''
+from clonedigger.debug import AST
+def getOriginalOffset(stmtSeq):
+    offset = 0
+    s = stmtSeq[0].getSourceLines()[0]
+    while s.find(" ")==0:
+        offset+=1
+        s = s[1:]
+    return offset
+
+def generateCodeSnippet(stmtSeq, filename):
+    file = open(filename, 'w')
+    offset = getOriginalOffset(stmtSeq)
+    for i in stmtSeq:
+        a = AST(i)
+        a.output("helper.out")
+        for j in i.getSourceLines():
+            file.write(j[offset:]+"\n")
+    file.close()
+
+if __name__ == '__main__':
+    pass

### 2014-03-14 EasyMerge/merger/unparse.py

@@ -1,0 +1,649 @@
+"Usage: unparse.py <path to source file>"
+import sys
+import ast
+import cStringIO
+import os
+
+# Large float and imaginary literals get turned into infinities in the AST.
+# We unparse those infinities to INFSTR.
+INFSTR = "1e" + repr(sys.float_info.max_10_exp + 1)
+
+def interleave(inter, f, seq):
+    """Call f on each item in seq, calling inter() in between.
+    """
+    seq = iter(seq)
+    try:
+        f(next(seq))
+    except StopIteration:
+        pass
+    else:
+        for x in seq:
+            inter()
+            f(x)
+
+class UTree:
+    def __init__(self,name=None):
+        self._name = name
+        self._attr = {}
+    def addAttr(self, attr, value):
+        self._attr[attr] = value
+        
+class Unifier:
+    def __init__(self, tree1, tree2):
+        self._t1 = tree1
+        self._t2 = tree2
+        self._utree = UTree()
+        self._utree = self.compare_trees(self._t1, self._t2)
+            
+    def compare_trees(self,t1,t2):
+        if self.check_entire_tree(t1,t2):
+            return t1
+        else:
+            if self.check_tree_name(t1, t2):
+                utree = UTree(t1.__class__.__name__)
+                return utree
+            else:
+                return "???" 
+        
+    def check_entire_tree(self,t1,t2):
+        if t1==t2:
+            return True
+        else:
+            return False
+    
+    def check_tree_name(self,t1,t2):
+        if t1.__class__.__name__==t2.__class__.__name__:
+            return True
+        else:
+            return False
+    
+    def check_value(self,v1,v2):
+        if v1==v2:
+            return True
+        else:
+            return False
+            
+class Unparser:
+    """Methods in this class recursively traverse an AST and
+    output source code for the abstract syntax; original formatting
+    is disregarded. """
+
+    def __init__(self, tree, file = sys.stdout):
+        """Unparser(tree, file=sys.stdout) -> None.
+         Print the source for tree to file."""
+        self.f = file
+        self.future_imports = []
+        self._indent = 0
+        self.dispatch(tree)
+        self.f.write("")
+        self.f.flush()
+
+    def fill(self, text = ""):
+        "Indent a piece of text, according to the current indentation level"
+        self.f.write("\n"+"    "*self._indent + text)
+
+    def write(self, text):
+        "Append a piece of text to the current line."
[…]

### 2014-03-14 EasyMerge/tests/Untitled Folder/autotag/mb.py

@@ -1,0 +1,397 @@
+# This file is part of beets.
+# Copyright 2013, Adrian Sampson.
+#
+# Permission is hereby granted, free of charge, to any person obtaining
+# a copy of this software and associated documentation files (the
+# "Software"), to deal in the Software without restriction, including
+# without limitation the rights to use, copy, modify, merge, publish,
+# distribute, sublicense, and/or sell copies of the Software, and to
+# permit persons to whom the Software is furnished to do so, subject to
+# the following conditions:
+#
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+"""Searches for albums in the MusicBrainz database.
+"""
+import logging
+import musicbrainzngs
+import re
+import traceback
+from urlparse import urljoin
+
+import beets.autotag.hooks
+import beets
+from beets import util
+from beets import config
+
+SEARCH_LIMIT = 5
+VARIOUS_ARTISTS_ID = '89ad4ac3-39f7-470e-963a-56509c546377'
+BASE_URL = 'http://musicbrainz.org/'
+
+musicbrainzngs.set_useragent('beets', beets.__version__,
+                             'http://beets.radbox.org/')
+
+class MusicBrainzAPIError(util.HumanReadableException):
+    """An error while talking to MusicBrainz. The `query` field is the
+    parameter to the action and may have any type.
+    """
+    def __init__(self, reason, verb, query, tb=None):
+        self.query = query
+        super(MusicBrainzAPIError, self).__init__(reason, verb, tb)
+
+    def get_message(self):
+        return u'"{0}" in {1} with query {2}'.format(
+            self._reasonstr(), self.verb, repr(self.query)
+        )
+
+log = logging.getLogger('beets')
+
+RELEASE_INCLUDES = ['artists', 'media', 'recordings', 'release-groups',
+                    'labels', 'artist-credits', 'aliases']
+TRACK_INCLUDES = ['artists', 'aliases']
+
+def track_url(trackid):
+    return urljoin(BASE_URL, 'recording/' + trackid)
+
+def album_url(albumid):
+    return urljoin(BASE_URL, 'release/' + albumid)
+
+def configure():
+    """Set up the python-musicbrainz-ngs module according to settings
+    from the beets configuration. This should be called at startup.
+    """
+    musicbrainzngs.set_hostname(config['musicbrainz']['host'].get(unicode))
+    musicbrainzngs.set_rate_limit(
[…]

### 2014-03-14 EasyMerge/tests/Untitled Folder/ui/__init__.py

@@ -1,0 +1,973 @@
+# This file is part of beets.
+# Copyright 2014, Adrian Sampson.
+#
+# Permission is hereby granted, free of charge, to any person obtaining
+# a copy of this software and associated documentation files (the
+# "Software"), to deal in the Software without restriction, including
+# without limitation the rights to use, copy, modify, merge, publish,
+# distribute, sublicense, and/or sell copies of the Software, and to
+# permit persons to whom the Software is furnished to do so, subject to
+# the following conditions:
+#
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+"""This module contains all of the core logic for beets' command-line
+interface. To invoke the CLI, just call beets.ui.main(). The actual
+CLI commands are implemented in the ui.commands module.
+"""
+from __future__ import print_function
+
+import locale
+import optparse
+import textwrap
+import sys
+from difflib import SequenceMatcher
+import logging
+import sqlite3
+import errno
+import re
+import struct
+import traceback
+
+from beets import library
+from beets import plugins
+from beets import util
+from beets.util.functemplate import Template
+from beets import config
+from beets.util import confit
+from beets.autotag import mb
+
+
+# On Windows platforms, use colorama to support "ANSI" terminal colors.
+
+if sys.platform == 'win32':
+    try:
+        import colorama
+    except ImportError:
+        pass
+    else:
+        colorama.init()
+
+
+
+# Constants.
+
+
+PF_KEY_QUERIES = {
+    'comp': 'comp:true',
+    'singleton': 'singleton:true',
+}
+
+# UI exception. Commands should throw this in order to display
+# nonrecoverable errors to the user.
+class UserError(Exception):
+    pass
+
+# Main logger.
+log = logging.getLogger('beets')
+
+
+
+# Utilities.
+
+
+def _encoding():
+    """Tries to guess the encoding used by the terminal."""
+    # Configured override?
+    encoding = config['terminal_encoding'].get()
+    if encoding:
+        return encoding
+
+    # Determine from locale settings.
+    try:
+        return locale.getdefaultlocale()[1] or 'utf8'
+    except ValueError:
+        # Invalid locale environment variable setting. To avoid
+        # failing entirely for no good reason, assume UTF-8.
+        return 'utf8'
+
+
+def decargs(arglist):
+    """Given a list of command-line argument bytestrings, attempts to
+    decode them to Unicode strings.
+    """
+    return [s.decode(_encoding()) for s in arglist]
+
+
+def print_(*strings):
[…]

### 2014-03-14 EasyMerge/tests/Untitled Folder/ui/commands.py

@@ -1,0 +1,1405 @@
+# This file is part of beets.
+# Copyright 2014, Adrian Sampson.
+#
+# Permission is hereby granted, free of charge, to any person obtaining
+# a copy of this software and associated documentation files (the
+# "Software"), to deal in the Software without restriction, including
+# without limitation the rights to use, copy, modify, merge, publish,
+# distribute, sublicense, and/or sell copies of the Software, and to
+# permit persons to whom the Software is furnished to do so, subject to
+# the following conditions:
+#
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+"""This module provides the default commands for beets' command-line
+interface.
+"""
+from __future__ import print_function
+
+import logging
+import os
+import time
+import itertools
+import codecs
+import platform
+
+import beets
+from beets import ui
+from beets.ui import print_, input_, decargs
+from beets import autotag
+from beets.autotag import recommendation
+from beets.autotag import hooks
+from beets import plugins
+from beets import importer
+from beets import util
+from beets.util import syspath, normpath, ancestry, displayable_path
+from beets.util.functemplate import Template
+from beets import library
+from beets import config
+from beets.util.confit import _package_path
+
+# Global logger.
+log = logging.getLogger('beets')
+
+# The list of default subcommands. This is populated with Subcommand
+# objects that can be fed to a SubcommandsOptionParser.
+default_commands = []
+
+
+
+# Utilities.
+
+
+def _do_query(lib, query, album, also_items=True):
+    """For commands that operate on matched items, performs a query
+    and returns a list of matching items and a list of matching
+    albums. (The latter is only nonempty when album is True.) Raises
+    a UserError if no items match. also_items controls whether, when
+    fetching albums, the associated items should be fetched also.
+    """
+    if album:
+        albums = list(lib.albums(query))
+        items = []
+        if also_items:
+            for al in albums:
+                items += al.items()
+
+    else:
+        albums = []
+        items = list(lib.items(query))
+
+    if album and not albums:
+        raise ui.UserError('No matching albums found.')
+    elif not album and not items:
+        raise ui.UserError('No matching items found.')
+
+    return items, albums
+
+
+
+# fields: Shows a list of available fields for queries and format strings.
+
+fields_cmd = ui.Subcommand('fields',
[…]

### 2014-03-14 EasyMerge/merger/unparse.py
new_unifier

@@ -27,6 +27,21 @@ class UTree:
         self._attr = {}
     def addAttr(self, attr, value):
         self._attr[attr] = value
+    def output(self,level,tree=None):
+        for i in range(level):
+            print "\t"
+        if tree==None:
+            print "Type:",self._name
+            for i in self._attr:
+                self.output(level+1,self._attr[i])
+        elif tree.__class__=="UTree":
+            print "Type:",tree._name
+            for i in tree._attr:
+                self.output(level+1,tree._attr[i])
+        else:
+            print "Other:",tree
+        
+        
         
 class Unifier:
     def __init__(self, tree1, tree2):
@@ -37,13 +52,62 @@ class Unifier:
             
     def compare_trees(self,t1,t2):
         if self.check_entire_tree(t1,t2):
+            print "t1=t2"
             return t1
         else:
             if self.check_tree_name(t1, t2):
+                print "t1,t2 have same type:",t1.__class__.__name__
                 utree = UTree(t1.__class__.__name__)
+                meth = getattr(self, "_"+t1.__class__.__name__)
+                (vals,nodes) = meth(t1,t2)
+                print nodes
+                for attr in nodes:
+                    node = nodes[attr]
+                    utree.addAttr(attr, self.compare_trees(node[0], node[1]))
+                if not vals and not nodes:
+                    print "t1,t2 have different numbers of attributes"
+                    return ("???",t1,t2)
+                
                 return utree
             else:
-                return "???" 
+                print "t1,t2 have different types:",t1.__class__.__name__,",",t2.__class__.__name__
+                return ("???",t1,t2)
+      
+    def _Module(self, t1,t2):
+        nodes = {}
+        if len(t1.body)!=len(t2.body):
+            return (None, None)
+        for i in range(len(t1.body)):
+            nodes["body["+str(i)+"]"]=[t1.body[i],t2.body[i]]
+        return ([],nodes)
+    
+    def _If(self, t1,t2):
+        node = {}
+        node["test"] = [t1.test, t2.test]
+        node["body"] = [t1.body, t2.body]
+        # collapse nested ifs into equivalent elifs.
+        elif_counter = -1
+        while True:
+            has_elif1 = t1.orelse and len(t1.orelse) == 1 and isinstance(t1.orelse[0], ast.If)
[…]

### 2014-03-16 EasyMerge/merger/SimpleStmtMerge.py
identical stmt in progress

@@ -8,9 +8,11 @@ import clonedigger.clonedigger as digger
 import clonedigger.anti_unification as anti_unification
 from clonedigger.abstract_syntax_tree import StatementSequence
 from clonedigger.debug import AST
+import clonedigger.debug as debug
 
 import test
 import type0_dealer
+import type1_dealer
 
 def sortDuplicates(duplicates):
     def f(a,b):
@@ -47,6 +49,52 @@ def mergeStmtSeqs(duplicates):
             pass
     print "Merged into",len(duplicate_set),"Sets"
     return duplicate_set
+
+def dup_class_fliter(duplicate_set):
+    filter = ["Class", "Import", "From","Return"]
+    rm_cluster = []
+    info = {0:[]}
+    for cluster in duplicate_set:
+        for id in range(len(cluster)):
+            seq = cluster[id]
+            rm_stmt = []
+            for ast in seq:
+                if ast.getName() in filter:
+                    rm_stmt.append(ast)
+            if len(rm_stmt)>0:
+                stmtSeq = []
+                orig_len = len(seq._sequence)
+                for stmt in rm_stmt:
+                    seq._sequence.remove(stmt)
+                if len(seq._sequence)==0:
+                    info[0].append(duplicate_set.index(cluster))                    
+                    rm_cluster.append(cluster)
+                    break
+                else:                    
+                    for stmt in seq:
+                        stmtSeq.append(stmt)
+                    stmtSeq = StatementSequence(stmtSeq)
+                    seq = stmtSeq
+                    reduction = (orig_len,len(seq._sequence))
+                    if reduction in info:
+                        if not duplicate_set.index(cluster) in info[reduction]:
+                            info[reduction].append(duplicate_set.index(cluster))
+                    else:
+                        info[reduction] = [duplicate_set.index(cluster)]
+                    
+    
+    for cluster in rm_cluster:
+        duplicate_set.remove(cluster) 
+    
+    print "cluster", info[0], "is full of invalid stmt"
+    for i in info:
+        if i==0:
+            continue
+        print "cluster", info[i],": Reduce",i[0],"stmt to",i[1],"stmt"
+    
+    
+    print "Filtered into", len(duplicate_set),"Sets"
+    return duplicate_set              
 
 def removeOverlappedSeqs(duplicate_set):
[…]

### 2014-03-16 EasyMerge/merger/clonedigger/debug.py

@@ -19,10 +19,13 @@ class AST:
         self.classes = []
         self.raw_call = []
         self.calls = []
+        self.var = []
         self.parse_tree(self.tree, [], self.raw_scope, self.raw_call, False)
+        self.parse_name(self.tree, self.var)
         self.process_imports()
         self.process_scope()
-        self.process_call()
+        self.process_call()  
+    
         
     def parse_tree(self, tree, scope, scope_result, call_result, in_call):
         if tree.getName() == "Import":
@@ -45,10 +48,38 @@ class AST:
         if tree.getName()=="CallFunc" and not in_call:
             in_call = True
             call_result.append((tree,(tree.getLineNumbers()[0], self.parse_call(tree.getChilds()[0]), scope)))
+            in_call = False
         for i in tree.getChilds():
             new_scope = list(scope)            
             self.parse_tree(i, scope, scope_result, call_result, in_call)
-            scope = new_scope    
+            scope = new_scope  
+            
+    def parse_name(self, tree, var, cur_line=None):
+        line_set = tree.getCoveredLineNumbers()
+        if len(line_set)>0:
+            cur_line = min(line_set)
+            cur_scope = self.findScope(cur_line)
+        if tree.getName() == "Name":
+            var.append((cur_line, tree.getChilds()[0].getName()[1:-1], cur_scope, 0))
+        if tree.getName() == "AssName":
+            if not tree.getParent().getName()=="For":
+                var.append((cur_line, tree.getChilds()[0].getName()[1:-1], cur_scope, 1))
+        for i in tree.getChilds():
+            self.parse_name(i, var)  
+    
+    def findScope(self,line):
+        scope = -1
+        inScope = False
+        for i in self.raw_scope:
+            (s,e) = i[-1][-1]
+            if s==e and s==-1:
+                continue
+            if line>=s and line<=e:
+                inScope = True
+                scope = self.raw_scope.index(i)
+            elif inScope:
+                return scope
+        return scope
             
     def parse_call(self,call):
         if call.getName()=="Name":
@@ -242,6 +273,10 @@ class Call:
         self.source = id
         
 
+def output_stmt_seq(seq):
+    for i in seq:
+        j = AST(i)
+        print j.visualizeTree(j.tree, 0)
         
         
         

### 2014-03-16 EasyMerge/merger/type1_dealer.py

@@ -1,0 +1,738 @@
+'''
+Created on Mar 15, 2014
+
+@author: h7qin
+'''
+"Usage: unparse.py <path to source file>"
+import sys
+import ast
+import cStringIO
+import os
+
+# Large float and imaginary literals get turned into infinities in the AST.
+# We unparse those infinities to INFSTR.
+INFSTR = "1e" + repr(sys.float_info.max_10_exp + 1)
+
+def interleave(inter, f, seq):
+    """Call f on each item in seq, calling inter() in between.
+    """
+    seq = iter(seq)
+    try:
+        f(next(seq))
+    except StopIteration:
+        pass
+    else:
+        for x in seq:
+            inter()
+            f(x)
+
+class Unparser:
+    """Methods in this class recursively traverse an AST and
+    output source code for the abstract syntax; original formatting
+    is disregarded. """
+
+    def __init__(self, tree, lines, src_ast, file = sys.stdout):
+        """Unparser(tree, file=sys.stdout) -> None.
+         Print the source for tree to file."""
+        self.calls = self.crop_calls(lines, src_ast)
+        self.variable, self.return_vars = self.crop_vars(lines, src_ast)
+        self.mod_calls = []
+        self.functions = src_ast.functions
+        self.classes = src_ast.classes
+        self.lines = lines
+        self.cur_call = -1        
+        self.incall = False
+        self.cur_str = ""
+        self.ret_str = False
+        self.top_level = True
+        self.args = []
+        
+        self.vars = []
+        self.rec_var = True 
+        self.is_func_name = False 
+        
+        self.f = file
+        
+        #for i in src_ast.raw_scope:
+        #    print i
+        
+        '''for i in self.calls:
+            self.f.write("=======================\n")
+            self.f.write("Name:"+str(i.name)+"\n")
+            self.f.write("line:"+str(i.line)+"\n")
+            self.f.write("scope:"+str(i.scope)+"\n")
+            self.f.write("source:"+str(i.source)+"\n")
+            self.f.write("tree:"+str(i.tree)+"\n")   '''
+         
+        self.f = file
+        self.future_imports = []
+        self._indent = 0
+        self.dispatch(tree)
+        self.f.write("\n")
+        self.f.flush()
+        
+        print "mod_calls:",self.mod_calls
+        print "new_vars:",self.vars
+        print "old_vars:",self.variable
+        if len(self.vars)!=len(self.variable):
+            print "ERROR"
[…]

### 2014-03-16 EasyMerge/tests/beets/mediafile.py

@@ -735,12 +735,15 @@ class VorbisImageStorageStyle(ListStorageStyle):
     def serialize(self, image):
         """Turn a Image into a base64 encoded FLAC picture block.
         """
+        a= 1+2+3
+        b=2+4+6
         pic = mutagen.flac.Picture()
         pic.data = image.data
         pic.type = image.type_index or 3  # Front cover
         pic.mime = image.mime_type
         pic.desc = image.desc or u''
-        return base64.b64encode(pic.write())
+        return pic
+        #base64.b64encode(pic.write())
 
 
 class FlacImageStorageStyle(ListStorageStyle):

### 2014-03-16 EasyMerge/tests/beets/ui/commands.py

@@ -232,7 +232,8 @@ def show_change(cur_artist, cur_album, match):
     # Data URL.
     if match.info.data_url:
         print_('URL:\n    %s' % match.info.data_url)
-
+    
+    
     # Info line.
     info = []
     # Similarity.

### 2014-03-16 paper/paper.tex

@@
 engineers. Even text-wise identical code clones can be semantically different when they are referring variables and calling functions outside. And the problem is more 
-complex when scopes and dependencies are considered. Furthermore, not all clones can be refactored as they may be part of tests or needed to maintain dependencies across multiple
-libraries. As a result, we need adaptive clone refactoring tools that can locate unnecessary clones and alert possible implications in the procedure to help
+complex when scopes and dependencies are involved. Furthermore, not all clones shall be refactored as they may be part of independent
+libraries. And refactoring is not only about removing duplicate code but also fixing all reference errors caused by such deletion thereafter. 
+As a result, we need adaptive clone refactoring tools that can locate unnecessary clones and alert possible implications in the procedure to help
 software engineers be more efficient and make less mistakes in the refactoring process.
@@
 refactors software projects written in Python. It adds intelligence to code clone refactoring by categorizing clones and generating refactoring recommendations
-based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone fragments in functions,
-classes, and across different scopes. It ensures functionality-wise consistency before and after refactoring and provide warnings when potential refactoring could lead to
+based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone fragments across different scopes. 
+It ensures functionality-wise consistency before and after refactoring and provide warnings when potential refactoring could lead to
 unwanted complexity or cause readability issues.
@@
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\category{D.2.7}{Software Engineering}{Maintenance}[Restructuring, reverse engineering, and reengineering]
 
-\terms{Software Engineering, Recommendation System}
+\terms{Algorithms}
 
-\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System, Python} % NOT required for Proceedings
+\keywords{Software engineering, clone detection, code refactoring, recommendation system, Python} % NOT required for Proceedings
 

### 2014-03-16 paper/paper.tex
paper update

@@
 have already been proposed. However, how to deal with detected clones, e.g. how to distinguish necessary clones from unnecessary ones and how to refactor code to remove
-unnecessary clones still remain a big problem in not only commercial but also academic domain. As a result, in this paper, we try to classify code clones and build
+unnecessary clones still remain a big problem in not only commercial but also academic domain. In this paper, we try to classify code clones and build
 a recommendation system called EasyMerge to help developers merge unnecessary clones on top of current state-of-the-art clone detection approach.
 
-More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detection approach. CloneDigger is one of the best available 
-clone detection tools currently for its overall performance, coverage of multiple clone types, and availability. 
-EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding and development.
+More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detector. CloneDigger is one of the best available 
+clone detection tools for its overall performance, coverage of multiple clone types, and availability. 
+EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding and reusing.
 
@@
 \subsection{Clone Refactoring}
-On the other hand, for clone refactoring, most proposed solutions use some pre-defined metrics as the refactoring guidance to help users determine whether the 
+On the other hand, for clone refactoring, most proposed solutions use pre-defined metrics as the refactoring guidance to help users determine whether the 
 code clones are suitable for refactoring. For example, Balazinska \cite{balazinska} proposed to use 21 metrics to measure the suitability for refactoring. Higo \cite{higo}
 developed ARIES tools, using the code detection tool CCFinder and environment analysis tool Gemini to find the clones can be refactored. And Schulze \cite{schulze}
-proposed a new metric DIST (distance of the code clones). Unlike them, instead of calculating distance between code fragments and only merging close clones, EasyMerge 
-try to fix the differences and merge as many clones as possible without introducing extra complexity.
+proposed a new metric DIST (distance of the code clones). 
+%Unlike them, instead of calculating distance between code fragments and only merging close clones, EasyMerge 
+%try to fix the differences and merge as many clones as possible without introducing extra complexity.
 
@@
 may contain function calls or variable references which are not defined inside the fragments. Furthermore, functions and variables of the same names may be in fact different
-at different locations of the code base. For example, if we have a code clone fragment as following:
+at different locations of the code base. For example, if we have a code clone fragment of following:
 
@@
 which could potentially cause reference errors. Secondly, when the length of the clone fragment is too long, we could possibly end up with a helper function of tons of parameters
-which in turn make the code after refactoring harder to understand and is against our goal to improve readability. And the most intuitive approach to solve the first problem
+which in turn make the code after refactoring harder to understand and is against our goal to improve readability. 
+For most clone refactoring approaches, this gives bad scores to the evaluation metrics and prevent merging. And a possible alternative approach
 is to return b and such variables from the ``Extracted Method" which introduces even more complexity.
 
-As a result, for recently proposed refactoring approach \cite{li} and the tools mentioned at the beginning of this subsection, they count the number of such external references
+For recently proposed refactoring approach \cite{li} and the tools mentioned at the beginning of this subsection, they count the number of such external references
 in a code clone fragment as the key factor of their refactoring guideline metrics. 
 And clone fragments of too many such occurrences will not be recommended for refactoring.
-Furthermore, in Li's work \cite{li}, after standardization, it can also be used to refactor semantical
+Furthermore, in Li's work \cite{li}, after standardization, it can also be used to refactor some semantical
 similar but syntax-wise different clones by moving different function references to extracted method's parameters.
+
+Additionally, results from clone detectors are usually clone pairs but it's very common 
+more than two fragments are clones of each other. Moreover, overlapping clone fragments often
+exist in large scale code bases, too.
+For example, it's not difficult to find a code block of ABCDEF where BC is a clone fragment of one other block and CDE is a clone fragment of another.
+For both cases, merging one set of clones will in turn break clones in another set.
+And we need to take care of all reference errors caused by code deletion. 
+Thus, our clone refactoring tool must handle all these potential issues without
+introducing too much computational overhead.
 
@@
 \section{CloneDigger}
+CloneDigger \cite{bulychev} was an anti-unification code clone detector introduced by Bulychev and Minea in 2008. It's one of the latest open source clone detection tool.
+
 \subsection{Overview}
@@
 \section{EasyMerge}
+\subsection{User Interface}
+
+\subsection{Preprocessing}
 

### 2014-03-16 EasyMerge/merger/Merge.py
first runnable

@@ -1,0 +1,18 @@
+'''
+Created on Mar 16, 2014
+
+@author: h7qin
+'''
+
+class Merge:
+    def __init__(self):
+        self._tag = []
+        self._code = ""
+        self._caller = {}
+    def add_code(self, code):
+        self._code = code
+    def add_tag(self, tag):
+        self._tag.append(tag)
+    def add_caller(self, tag, caller):
+        self._caller[tag] = caller
+        

### 2014-03-16 EasyMerge/merger/helper.py

@@ -1,16 +1,0 @@
-class T:
-    def __init__(self):
-        self.t = "t"
-t = T()
-if val is None:
-    return 0.0
-elif isinstance(val, int) or isinstance(val, float):
-    return float(val)
-else:
-    if not isinstance(val, basestring):
-        val = unicode(val)
-    val = re.match(r'[\+-]?[0-9\.]*', val.strip()).group(0)
-    if not val:
-        return 0.0
-    else:
-        return float(val)

### 2014-03-16 EasyMerge/merger/helper2.py

@@ -1,12 +1,0 @@
-if val is None:
-    return 0
-elif isinstance(val, int) or isinstance(val, float):
-    return int(val)
-else:
-    if not isinstance(val, basestring):
-        val = unicode(val)
-    val = re.match(r'[\+-]?[0-9\.]*', val.strip()).group(0)
-    if not val:
-        return 0
-    else:
-        return int(val)

### 2014-03-16 EasyMerge/merger/merger.py

@@ -8,11 +8,13 @@ import clonedigger.clonedigger as digger
 import clonedigger.anti_unification as anti_unification
 from clonedigger.abstract_syntax_tree import StatementSequence
 from clonedigger.debug import AST
-import clonedigger.debug as debug
+#import clonedigger.debug as debug
 
-import test
+from Merge import Merge 
 import type0_dealer
 import type1_dealer
+
+mergeResults = []
 
 def sortDuplicates(duplicates):
     def f(a,b):
@@ -308,59 +310,72 @@ def tmpDistributor(dSet, dInfo, src_ast_list):
         #print info, len(cluster)#, ":", tagging(cluster[0])
         if info[0]=="Def" and info[1]<=0:
             print "Type0"
-            (caller,code) = processIdenticalDef(src_ast_list, cluster)
-            #print code
-            #for s in cluster:
-                #print tagging(s),":"
-                #print caller[tagging(s)]
+            if processIdenticalDef(src_ast_list, cluster):
+                print "Success"
+            else:
+                print "Error"
+            #break   
         if info[0]=="Stmt" and info[1]<=0:
             print "Type1"
-            processIdenticalStmt(src_ast_list, cluster)
-            #break
-            '''print code
-            for s in cluster:
-                print tagging(s),":"
-                print caller[tagging(s)]'''
+            if processIdenticalStmt(src_ast_list, cluster, i):
+                print "Success"
+            else:
+                print "Error"#break
+
+        
 
 def processIdenticalDef(src_ast_list, cluster):
     caller = {}
     merged_code = []
     for i in cluster:
         filename = i.getSourceFile().getFileName()
-        src_ast_list[str(filename)].output("./sandbox/test.out")
+        #src_ast_list[str(filename)].output("./sandbox/test.out")
         lines = tagging(i)[1:]
         code_snippet = generateCodeSnippet(i)
         merged = type0_dealer.generateNewCode(code_snippet, lines, src_ast_list[str(filename)])
         merged_code.append(merged.get_code())
         caller[tagging(i)]=merged.caller
+        
     for i in merged_code[1:]:
         if i!=merged_code[0]:
-            print "ERROR"
-            return (None,None)
-    return (caller,merged_code[0])
-        #print i
-        #print merged_code[0]
+            return False
+        
+    code = merged_code[0]
+    m = Merge()
[…]

### 2014-03-16 EasyMerge/merger/sandbox/test.py

@@ -1,24 +1,0 @@
-def represent_mapping(self, tag, mapping, flow_style=None):
-    value = []
-    node = yaml.MappingNode(tag, value, flow_style=flow_style)
-    if self.alias_key is not None:
-        self.represented_objects[self.alias_key] = node
-    best_style = True
-    if hasattr(mapping, 'items'):
-        mapping = list(mapping.items())
-    for item_key, item_value in mapping:
-        node_key = self.represent_data(item_key)
-        node_value = self.represent_data(item_value)
-        if not (isinstance(node_key, yaml.ScalarNode) and \
-                not node_key.style):
-            best_style = False
-        if not (isinstance(node_value, yaml.ScalarNode) and \
-                not node_value.style):
-            best_style = False
-        value.append((node_key, node_value))
-    if flow_style is None:
-        if self.default_flow_style is not None:
-            node.flow_style = self.default_flow_style
-        else:
-            node.flow_style = best_style
-    return node

### 2014-03-16 EasyMerge/merger/sandbox/tmp.py

@@ -1,6 +1,0 @@
-
-pic = mutagen.flac.Picture()
-pic.data = image.data
-pic.type = (image.type_index or 3)
-pic.mime = image.mime_type
-pic.desc = (image.desc or u'')

### 2014-03-16 EasyMerge/merger/test.py

@@ -1,35 +1,0 @@
-'''
-Created on Mar 14, 2014
-
-@author: h7qin
-'''
-from clonedigger.debug import AST
-def getOriginalOffset(stmtSeq):
-    offset = 0
-    s = stmtSeq[0].getSourceLines()[0]
-    while s.find(" ")==0:
-        offset+=1
-        s = s[1:]
-    return offset
-
-def generateCodeSnippet(stmtSeq, filename=None):
-    if filename!=None:
-        file = open(filename, 'w')
-    else:
-        s = ""
-    offset = getOriginalOffset(stmtSeq)
-    for i in stmtSeq:
-        a = AST(i)
-        #a.output("helper.out")
-        for j in i.getSourceLines():
-            if filename!=None:
-                file.write(j[offset:]+"\n")
-            else:
-                s+=(j[offset:]+"\n")    
-    if filename!=None:          
-        file.close()
-    else:
-        return s
-
-if __name__ == '__main__':
-    pass

### 2014-03-16 EasyMerge/merger/type1_dealer.py

@@ -25,6 +25,154 @@ def interleave(inter, f, seq):
         for x in seq:
             inter()
             f(x)
+            
+class Code:
+    s = ""
+    def __init__(self, id):
+        self.id = id
+    def write(self, s):
+        self.s+=s
+    def flush(self):
+        pass
+    def split(self):
+        self.code_lines = self.s.splitlines()
+        #self.code_lines = filter(lambda a: a != "", self.code_lines)
+        while self.code_lines[0]=="":
+            self.code_lines = self.code_lines[1:]
+            
+    def add_parameter(self, unreachable, vars):
+        param = [] 
+        
+        def add_unreachable(unreachable):
+            s = "["
+            for i in unreachable:
+                s+=(i+", ")
+            s=s[:-2]+"]"
+            return s
+    
+        def merge_vars(vars):
+            var_dict = {}
+            for i in vars:
+                if i=="":
+                    continue
+                var_dict[i]=1
+            return var_dict                
+        
+        if len(unreachable)>0:
+            param.append("unreachable_method")
+            self.unreachable = add_unreachable(unreachable)
+        else:
+            self.unreachable = None
+
+        self.vars = merge_vars(vars)
+        for i in self.vars:
+            param.append(i)
+        
+        self.param = param
+
+    def write_head_line(self,unreachable, vars):
+        self.add_parameter(unreachable, vars)
+        func_name = "helper"+str(self.id)
+        if len(self.param)>0:
+            param = "("
+            for i in self.param:
+                param += i+", "
+            param = param[:-2]+")"
+        else:
+            param = "()"
+        headline = "def "+func_name+param+":"
+        for i in range(len(self.code_lines)):
+            self.code_lines[i] = "    "+self.code_lines[i]
+        self.code_lines = [headline]+self.code_lines
+        
+    def add_rets(self, return_vars):
+        def merge_vars(vars):
+            var_dict = {}
+            for i in vars:
+                var_dict[i[1]]=1
+            return var_dict
+        ret_vars = []
+        for i in merge_vars(return_vars):
+            ret_vars.append(i)
+        self.return_vars = ret_vars
+        
+        
+    def write_return_line(self,return_vars):
+        
+        self.add_rets(return_vars)
+        
+        ret_line = "    return ("
+        if len(self.return_vars)>1:
+            for i in self.return_vars:
[…]

### 2014-03-16 EasyMerge/merger/clonedigger/clonedigger.py
bug_fix

@@ -33,7 +33,8 @@ import arguments
 import html_report
 import debug
 
-def main(cmdline):
+def main(cmdline, dir=None):
+    print dir
    
     cmdline.add_option('-l', '--language', dest='language',
                        type='choice', choices=['python', 'java', 'lua', 'javascript', 'js'],
@@ -95,6 +96,11 @@ def main(cmdline):
                          **arguments.__dict__)
 
     (options, source_file_names) = cmdline.parse_args()
+    
+    if dir:
+        source_file_names = [dir]
+    print source_file_names
+    
     if options.f_prefixes != None:
        func_prefixes = tuple([x.strip() for x in options.f_prefixes.split(',')])
     else:

### 2014-03-16 EasyMerge/merger/merger.py

@@ -136,7 +136,7 @@ def removeOverlappedSeqs(duplicate_set):
     
     print len(duplicate_set),"sets left"
 
-def getCloneStmt():
+def getCloneStmt(dir):
     print "========================================"
     print "Using Clonedigger to detect duplicate codes"
     print "========================================"
@@ -152,7 +152,7 @@ Don't forget to remove automatically generated sources, tests and third party li
 Notice:
 The semantics of threshold options is discussed in the paper "Duplicate code detection using anti-unification", which can be downloaded from the site http://clonedigger.sourceforge.net . All arguments are optional. Supported options are: 
 """)
-    (src_ast_list, orig_duplicates) = digger.main(cmdline)
+    (src_ast_list, orig_duplicates) = digger.main(cmdline, dir)
     sortDuplicates(orig_duplicates)
     duplicate_set = mergeStmtSeqs(orig_duplicates)
     duplicate_set = dup_class_fliter(duplicate_set) 
@@ -406,14 +406,14 @@ def generateCodeSnippet(stmtSeq, filename=None):
     else:
         return s
         
-def main():
-    (src_ast_list, duplicate_set) = getCloneStmt()
+def main(dir):
+    (src_ast_list, duplicate_set) = getCloneStmt(dir)
     (dSetInfoList, duplicate_set) = refineDuplicateSet(duplicate_set)
     tmpDistributor(duplicate_set, dSetInfoList, src_ast_list)
     return mergeResults
 
 if __name__ == '__main__':
-    main()
+    main("../tests/beets")
     
     
     

### 2014-03-16 EasyMerge/clonedigger/clonedigger.py
bug fix

@@ -34,7 +34,6 @@ import html_report
 import debug
 
 def main(cmdline, dir=None):
-    print dir
    
     cmdline.add_option('-l', '--language', dest='language',
                        type='choice', choices=['python', 'java', 'lua', 'javascript', 'js'],
@@ -99,8 +98,6 @@ def main(cmdline, dir=None):
     
     if dir:
         source_file_names = [dir]
-    print source_file_names
-    
     if options.f_prefixes != None:
        func_prefixes = tuple([x.strip() for x in options.f_prefixes.split(',')])
     else:

### 2014-03-16 EasyMerge/merger/Result.py

@@ -4,7 +4,7 @@ Created on Mar 16, 2014
 @author: h7qin
 '''
 
-class Merge:
+class Result:
     def __init__(self):
         self._tag = []
         self._code = ""
@@ -15,4 +15,9 @@ class Merge:
         self._tag.append(tag)
     def add_caller(self, tag, caller):
         self._caller[tag] = caller
+    def output(self):
+        print self._code
+        for i in self._caller:
+            print i,":"
+            print self._caller[i]
         

### 2014-03-16 EasyMerge/merger/merger.py

@@ -10,7 +10,7 @@ from clonedigger.abstract_syntax_tree import StatementSequence
 from clonedigger.debug import AST
 #import clonedigger.debug as debug
 
-from Merge import Merge 
+from Result import Result 
 import type0_dealer
 import type1_dealer
 
@@ -341,7 +341,7 @@ def processIdenticalDef(src_ast_list, cluster):
             return False
         
     code = merged_code[0]
-    m = Merge()
+    m = Result()
     m.add_code(code)
     for s in cluster:
         tag = tagging(s)
@@ -368,7 +368,7 @@ def processIdenticalStmt(src_ast_list, cluster, id):
             return False
         
     code = merged_code[0]
-    m = Merge()
+    m = Result()
     m.add_code(code)
     for s in cluster:
         tag = tagging(s)
@@ -414,6 +414,9 @@ def main(dir):
 
 if __name__ == '__main__':
     main("../tests/beets")
+    for i in mergeResults:
+        i.output()
+        print ''
     
     
     

### 2014-03-16 EasyMerge/merger/merger.py
process diff in progress

@@ -307,7 +307,7 @@ def tmpDistributor(dSet, dInfo, src_ast_list):
     for i in range(len(dSet)):
         cluster = dSet[i]
         info = dInfo[i]
-        #print info, len(cluster)#, ":", tagging(cluster[0])
+        print info, len(cluster)#, ":", tagging(cluster[0])
         if info[0]=="Def" and info[1]<=0:
             print "Type0"
             if processIdenticalDef(src_ast_list, cluster):
@@ -341,6 +341,7 @@ def processIdenticalDef(src_ast_list, cluster):
             return False
         
     code = merged_code[0]
+    print code
     m = Result()
     m.add_code(code)
     for s in cluster:
@@ -353,6 +354,7 @@ def processIdenticalDef(src_ast_list, cluster):
 
 def processIdenticalStmt(src_ast_list, cluster, id):
     caller = {}
+    merged_list = []
     merged_code = []
     for i in cluster:     
         filename = i.getSourceFile().getFileName()
@@ -360,11 +362,26 @@ def processIdenticalStmt(src_ast_list, cluster, id):
         lines = tagging(i)[1:]
         code_snippet = generateCodeSnippet(i)
         merged = type1_dealer.generateNewCode(id, code_snippet, lines, src_ast_list[str(filename)])
+        merged_list.append(merged)
         merged_code.append(merged.get_code())
         caller[tagging(i)]=merged.caller
         
-    for i in merged_code[1:]:
-        if i!=merged_code[0]:
+    for i in range(1,len(merged_list)):
+        cur_merge = merged_list[i]
+        cur_code = merged_code[i]
+        if cur_code!=merged_code[0]:
+            print "DIFFERENT!"
+            if cur_merge.code_lines[1:-1]!=merged_list[0].code_lines[1:-1]:
+                print "STILL_DIFF"
+                for j in merged_code:
+                    print j
+                    print ""
+            else:
+                print cur_merge.param
+                print merged_list[0].param
+                print cur_merge.return_vars
+                print merged_list[0].return_vars
+                
             return False
         
     code = merged_code[0]

### 2014-03-16 EasyMerge/merger/type0_dealer.py

@@ -26,17 +26,16 @@ class Code:
     def add_parameter(self, unreachable):  
         
         def add_unreachable(unreachable):
-            s = "["
+            d = {}
             for i in unreachable:
-                s+=(i+", ")
-            s=s[:-2]+"]"
-            return s     
+                d[i]=1
+            return d  
          
         if len(unreachable)==0:
             self.unreachable = None
             return
         else:
-            self.unreachable = add_unreachable(unreachable)                   
+            self.unreachable = add_unreachable(unreachable)                  
         
         line = self.code_lines[0]
         if not line.startswith("def"):
@@ -44,10 +43,15 @@ class Code:
         ismember = False
         if line[line.find("(")+1:].startswith("self"):
             ismember = True
+        
+        unreachable_param = ""
+        for i in self.unreachable:
+            unreachable_param+=(i+", ") 
+        
         if ismember:
-            self.code_lines[0] = line.replace("(self,", "(self, unreachable_method,")
+            self.code_lines[0] = line.replace("(self,", "(self, "+unreachable_param)
         else:
-            self.code_lines[0] = line = line[:line.find("(")+1]+"unreachable_method, "+line[line.find("(")+1:]
+            self.code_lines[0] = line = line[:line.find("(")+1]+unreachable_param+line[line.find("(")+1:]
     
 
     def get_caller(self, args):
@@ -55,28 +59,33 @@ class Code:
         if not line.startswith("def"):
             print "invalid code snippet"
                        
-        if self.unreachable:
+        '''if self.unreachable:
             s1 = "unreachable = "+self.unreachable
         else:
-            s1 = ""
+            s1 = ""'''
+        s1 = ""
             
         def get_func_name():
             line = self.code_lines[0]
             if not line.startswith("def"):
                 print "invalid code snippet"
+            orig_name = line[4:line.find("(")].strip()
             self.func_name = line[4:line.find("(")].strip()+"_helper"
+            self.code_lines[0] = line [:4]+self.func_name+line[line.find("("):]
                     
         get_func_name()
         s2 = "return "
         s2 += self.func_name
         s2 += "("
         if self.unreachable:
-            args = args[:args.index("self")+1]+["unreachable"]+args[args.index("self")+1:]
+            args = args[:args.index("self")+1]+self.unreachable.keys()+args[args.index("self")+1:]
             
         for i in args:
             s2 += (i+", ")
         s2 = s2[:-2]+")"
[…]

### 2014-03-16 EasyMerge/merger/type1_dealer.py

@@ -44,11 +44,18 @@ class Code:
         param = [] 
         
         def add_unreachable(unreachable):
-            s = "["
+            #refine code
+            for i in range(len(self.code_lines)):
+                while "unreachable_method" in self.code_lines[i]:
+                    orig_str = self.code_lines[i][self.code_lines[i].find("unreachable_method"):]
+                    orig_str = orig_str[:orig_str.find("]")+1]
+                    id = int(orig_str[orig_str.find("[")+1:-1])
+                    func_name = unreachable[id]
+                    self.code_lines[i] = self.code_lines[i].replace(orig_str,func_name) 
+            d = {}
             for i in unreachable:
-                s+=(i+", ")
-            s=s[:-2]+"]"
-            return s
+                d[i]=1
+            return d 
     
         def merge_vars(vars):
             var_dict = {}
@@ -59,10 +66,13 @@ class Code:
             return var_dict                
         
         if len(unreachable)>0:
-            param.append("unreachable_method")
             self.unreachable = add_unreachable(unreachable)
+            for i in self.unreachable:
+                param.append(i)
         else:
             self.unreachable = None
+        
+        print self.unreachable
 
         self.vars = merge_vars(vars)
         for i in self.vars:
@@ -146,10 +156,10 @@ class Code:
 
     def get_caller(self):
 
-        if self.unreachable:
+        '''if self.unreachable:
             s1 = "unreachable = "+self.unreachable
         else:
-            s1 = ""
+            s1 = ""'''
             
         func_name = "helper"+str(self.id)
         
@@ -158,7 +168,7 @@ class Code:
             s2 += self.receiver+" = "
         s2 += self.code_lines[0][4:-1]
 
-        self.caller = [s1,s2]
+        self.caller = s2
     
     def get_code(self):
         s = ""
@@ -285,7 +295,7 @@ class Unparser:
     def call_dealer(self,tree):
         #self.write("CALL_HERE"+str(tree.lineno)+","+str(tree.col_offset))
         
-        def process_mod_call(call):            
+        def process_mod_call(call):  
             self.write("unreachable_method["+str(len(self.mod_calls))+"]")
             #self.write("$CALL:"+str(call.source)+"$")
             self.mod_calls.append(call)
@@ -599,7 +609,11 @@ class Unparser:
         #if t.id=="ui":
             #print "ui=======",self.rec_var
         if self.rec_var:            
-            if not self.is_func_name:                
+            if not self.is_func_name: 
+                '''print self.variable 
[…]

### 2014-03-16 EasyMerge/clonedigger/clonedigger.py
add param threshold

@@ -33,7 +33,7 @@ import arguments
 import html_report
 import debug
 
-def main(cmdline, dir=None):
+def main(cmdline, dir=None, custom_distance_threshold=None):
    
     cmdline.add_option('-l', '--language', dest='language',
                        type='choice', choices=['python', 'java', 'lua', 'javascript', 'js'],
@@ -132,6 +132,9 @@ def main(cmdline, dir=None):
         arguments.distance_threshold = supplier.distance_threshold
     if options.size_threshold is None:
         arguments.size_threshold = supplier.size_threshold
+        
+    if custom_distance_threshold:
+        arguments.distance_threshold = custom_distance_threshold
     
     report.startTimer('Construction of AST')
     

### 2014-03-16 EasyMerge/merger/merger.py

@@ -136,7 +136,7 @@ def removeOverlappedSeqs(duplicate_set):
     
     print len(duplicate_set),"sets left"
 
-def getCloneStmt(dir):
+def getCloneStmt(dir,distance_threshold):
     print "========================================"
     print "Using Clonedigger to detect duplicate codes"
     print "========================================"
@@ -152,7 +152,7 @@ Don't forget to remove automatically generated sources, tests and third party li
 Notice:
 The semantics of threshold options is discussed in the paper "Duplicate code detection using anti-unification", which can be downloaded from the site http://clonedigger.sourceforge.net . All arguments are optional. Supported options are: 
 """)
-    (src_ast_list, orig_duplicates) = digger.main(cmdline, dir)
+    (src_ast_list, orig_duplicates) = digger.main(cmdline, dir, distance_threshold)
     sortDuplicates(orig_duplicates)
     duplicate_set = mergeStmtSeqs(orig_duplicates)
     duplicate_set = dup_class_fliter(duplicate_set) 
@@ -423,8 +423,8 @@ def generateCodeSnippet(stmtSeq, filename=None):
     else:
         return s
         
-def main(dir):
-    (src_ast_list, duplicate_set) = getCloneStmt(dir)
+def main(dir,distance_threshold):
+    (src_ast_list, duplicate_set) = getCloneStmt(dir,distance_threshold)
     (dSetInfoList, duplicate_set) = refineDuplicateSet(duplicate_set)
     tmpDistributor(duplicate_set, dSetInfoList, src_ast_list)
     return mergeResults

### 2014-03-16 EasyMerge/main.py
updates to UI

@@ -11,6 +11,6 @@ from PyQt4 import QtGui
 if __name__ == '__main__':
     app = QtGui.QApplication(sys.argv)
     bg = Background()
-    bg.setWindowTitle('EasyMerge - Clone Merger')
+    bg.setWindowTitle('EasyMerge - Clone Refactor')
     bg.showMaximized()
     sys.exit(app.exec_())

### 2014-03-16 EasyMerge/merger/Result.py

@@ -15,9 +15,13 @@ class Result:
         self._tag.append(tag)
     def add_caller(self, tag, caller):
         self._caller[tag] = caller
+    def get_code(self):
+        return self._code
+    def get_caller(self):
+        return self._caller
     def output(self):
         print self._code
         for i in self._caller:
             print i,":"
             print self._caller[i]
-        
+

### 2014-03-16 EasyMerge/merger/analyzer.py

@@ -1,0 +1,7 @@
+import merger
+
+
+class Analyzer():
+    def analyze(self, path):
+        print 'Analyzing ' + path + '...'
+        return merger.main(path, 5)

### 2014-03-16 EasyMerge/ui/background.py

@@ -1,5 +1,8 @@
 from PyQt4 import QtGui
 from tmp.dummy import Dummy
+from merger.analyzer import Analyzer
+import os
+from merger.Result import Result
 
 class Background(QtGui.QWidget):
     def __init__(self):
@@ -18,6 +21,7 @@ class Background(QtGui.QWidget):
         self._sets = []
         self.initUI()
 
+
     def initUI(self):
         grid = QtGui.QGridLayout()
         grid.addWidget(self._open, 0, 0, 1, 1)
@@ -32,8 +36,6 @@ class Background(QtGui.QWidget):
         box.addWidget(self._merge)
         box.addWidget(self._unmerge)
         grid.addLayout(box, 3, 0, 1, 1)
-
-        #grid.addWidget(self._merge, 3, 0, 1, 1)
 
         grid.setColumnStretch(0, 1)
         grid.setColumnStretch(1, 3)
@@ -61,25 +63,66 @@ class Background(QtGui.QWidget):
             msg.exec_()
         else:
             #analyze
-            sets = Dummy().do()
-            self.updateUI(sets)
+            analyzer = Analyzer()
+            result = analyzer.analyze(self._path)
+            self.updateUI(result)
 
     def updateUI(self, sets):
         self._sets = sets
         self._list.clear()
+        counter = 1
         for set in sets:
-            item = QtGui.QListWidgetItem(str(set))
+            item = QtGui.QListWidgetItem('Merge ' + str(counter))
             item.setForeground(QtGui.QColor('red'))
             self._list.addItem(item)
+            counter += 1
+
+    def populateTabs(self, sets):
+        self._tabs.clear()
+        counter = 0
+        for key in sets:
+            title = key[0]
+            start = key[1]
+            end = key[2]
+            replacement = str(sets[key])
+            text = self.generateText(title, start, end, replacement)
+            self._tabs.addTab(text, os.path.split(title)[1])
+            self._tabs.setTabToolTip(counter, title)
+            counter += 1
+
+    def generateText(self, title, start, end, replacement):
+        browser = QtGui.QTextBrowser(self)
+        f = open(title)
+        lines = f.readlines()
+        counter = 0
+        for line in lines:
+            indent = ''
+            for i in range(0, 6 - len(str(counter))):
+                indent += ' '
+            indent += str(counter) + ':    '
+            browser.insertPlainText(indent + line)
+            counter += 1
+
+        block = browser.document().findBlockByLineNumber(start + 15)
[…]

### 2014-03-16 EasyMerge/ui/background.py
update ui

@@ -67,6 +67,17 @@ class Background(QtGui.QWidget):
             result = analyzer.analyze(self._path)
             self.updateUI(result)
 
+
+    def resetInfo(self, text):
+        self._info.clear()
+        self._info.insertPlainText(text)
+
+    def appendInfo(self, text):
+        self._info.insertPlainText(text)
+
+    def clearInfo(self, text):
+        self._info.clear()
+
     def updateUI(self, sets):
         self._sets = sets
         self._list.clear()

### 2014-03-17 paper/paper.tex
paper update
paper updates

@@
 \section{EasyMerge}
+The entire EasyMerge program is written with Python 2.7.5 and the user interface is powered by PyQt 4.10.4.
+It takes a folder of Python written source tree as input, look for all refactorable clones and recommend potential merges.
+
 \subsection{User Interface}
+EasyMerge has a simple and straightforward user interface, as shown in figure.
 
 \subsection{Preprocessing}
+The first step of EasyMerge is to run CloneDigger at target source tree, take its output and format and standardize it for our own usage.
+The core of this step is to classify code clones and get the ones that we not only can but also want to merge.
 

### 2014-03-17 EasyMerge/ui/background.py

@@ -10,7 +10,8 @@ class Background(QtGui.QWidget):
         self._list = QtGui.QListWidget(self)
         self._tabs = QtGui.QTabWidget(self)
         self._result = QtGui.QTextBrowser(self)
-        self._info = QtGui.QTextBrowser(self)
+        self._log = QtGui.QTextBrowser(self)
+        self._eval = QtGui.QTextBrowser(self)
         self._merge = QtGui.QPushButton('Merge', self)
         self._unmerge = QtGui.QPushButton('Unmerge', self)
         self._analyze = QtGui.QPushButton('Analyze', self)
@@ -20,6 +21,9 @@ class Background(QtGui.QWidget):
         self._path = ''
         self._sets = []
         self.initUI()
+        self.log('EasyMerge started')
+        self.log('UI initialization completed')
+        self.log('Please pick source tree to analyze')
 
 
     def initUI(self):
@@ -30,12 +34,19 @@ class Background(QtGui.QWidget):
         grid.addWidget(self._list, 1, 0, 1, 1)
         grid.addWidget(self._tabs, 1, 1, 1, 2)
         grid.addWidget(self._result, 2, 1, 2, 2)
-        grid.addWidget(self._info, 2, 0, 1, 1)
+        #grid.addWidget(self._info, 2, 0, 1, 1)
 
+        #merge and unmerge buttons
         box = QtGui.QBoxLayout(QtGui.QBoxLayout.LeftToRight)
         box.addWidget(self._merge)
         box.addWidget(self._unmerge)
         grid.addLayout(box, 3, 0, 1, 1)
+
+        #log and eval
+        box2 = QtGui.QBoxLayout(QtGui.QBoxLayout.TopToBottom)
+        box2.addWidget(self._log)
+        box2.addWidget(self._eval)
+        grid.addLayout(box2, 2, 0, 1, 1)
 
         grid.setColumnStretch(0, 1)
         grid.setColumnStretch(1, 3)
@@ -49,6 +60,8 @@ class Background(QtGui.QWidget):
         self._unmerge.clicked.connect(self.unmergeClicked)
         self._list.itemClicked.connect(self.listClicked)
 
+    def log(self, text):
+        self._log.insertPlainText(text + '\n')
 
     def openClicked(self):
         sender = self.sender()
@@ -63,20 +76,11 @@ class Background(QtGui.QWidget):
             msg.exec_()
         else:
             #analyze
+            self.log('Start running CloneDigger...')
[…]

### 2014-03-17 EasyMerge/clonedigger/abstract_syntax_tree.py
bug_fix

@@ -101,8 +101,21 @@ class AbstractSyntaxTree:
         source_line_numbers = self.getCoveredLineNumbers()
         source_line_numbers_list = list(range(min(source_line_numbers), max(source_line_numbers)+1))
         source_line_numbers_list.sort()
+        
         for source_line_number in source_line_numbers_list:
             r.append(self.getSourceFile().getSourceLine(source_line_number) ) 
+        
+        i=1
+        bug = [")","]","}"]
+        while len(self.getSourceFile()._source_lines)>max(source_line_numbers)+i:
+            last_line = max(source_line_numbers)+i
+            #print "LAST LINE = ",self.getSourceFile().getSourceLine(last_line) 
+            if self.getSourceFile().getSourceLine(last_line).strip() in bug:                
+                r.append(self.getSourceFile().getSourceLine(last_line) )
+            else:
+                break
+            i+=1
+
         return r
     def getName(self):
         return self._name

### 2014-03-17 EasyMerge/merger/merger.py

@@ -478,8 +478,13 @@ def generateCodeSnippet(stmtSeq, filename=None):
     offset = getOriginalOffset(stmtSeq)
     for i in stmtSeq:
         a = AST(i)
-        #a.output("helper.out")
+        '''print "ORIG CODE:"
         for j in i.getSourceLines():
+            print j'''
+        #a.output("helper.out")
+        #print "\nNEW CODE"
+        for j in i.getSourceLines():
+            #print j[offset:]
             if filename!=None:
                 file.write(j[offset:]+"\n")
             else:

### 2014-03-17 EasyMerge/clonedigger/abstract_syntax_tree.py
bug fix

@@ -106,12 +106,16 @@ class AbstractSyntaxTree:
             r.append(self.getSourceFile().getSourceLine(source_line_number) ) 
         
         i=1
-        bug = [")","]","}"]
+        bug = [")","]","}",","]
         while len(self.getSourceFile()._source_lines)>max(source_line_numbers)+i:
-            last_line = max(source_line_numbers)+i
-            #print "LAST LINE = ",self.getSourceFile().getSourceLine(last_line) 
-            if self.getSourceFile().getSourceLine(last_line).strip() in bug:                
-                r.append(self.getSourceFile().getSourceLine(last_line) )
+            last_lineno = max(source_line_numbers)+i
+            last_line = self.getSourceFile().getSourceLine(last_lineno).strip().replace(" ","")
+            buggy = True
+            for s in last_line:
+                if s not in bug:
+                    buggy = False
+            if buggy:
+                r.append(self.getSourceFile().getSourceLine(last_lineno) )
             else:
                 break
             i+=1

### 2014-03-17 EasyMerge/merger/merger.py

@@ -445,9 +445,9 @@ def processNonIdenticalStmt(src_ast_list, cluster, id):
     for i in range(1,len(merged_list)):
         cur_code = merged_code[i]
         if cur_code!=merged_code[0]:
-            print "DIFFERENT!"
-            for m in merged_list:
-                m.output()
+            print "UNMERGABLELY DIFFERENT!"
+            #for m in merged_list:
+            #    m.output()
             return False
            
     code = merged_code[0]
@@ -501,7 +501,7 @@ def main(dir,distance_threshold):
     return mergeResults
 
 if __name__ == '__main__':
-    main("../tests/beets", 10)
+    main("../tests/wagtail", 10)
     for i in mergeResults:
         i.output()
         print ''

### 2014-03-17 EasyMerge/merger/type0_dealer.py

@@ -78,7 +78,10 @@ class Code:
         s2 += self.func_name
         s2 += "("
         if self.unreachable:
-            args = args[:args.index("self")+1]+self.unreachable.keys()+args[args.index("self")+1:]
+            if "self" in args:
+                args = args[:args.index("self")+1]+self.unreachable.keys()+args[args.index("self")+1:]
+            else:
+                args = self.unreachable.keys()+args
             
         for i in args:
             s2 += (i+", ")

### 2014-03-17 paper/paper.tex
update

@@
 
+\begin{figure*}
+\centering
+\epsfig{file=screen.pdf}
+\caption{EasyMerge User Interface}
+\end{figure*}
+
 \subsection{Duplicate Code Detection Algorithm}
@@
 \subsection{User Interface}
-EasyMerge has a simple and straightforward user interface, as shown in figure.
+EasyMerge has a simple and straightforward user interface, as shown in {\bf Figure 1}.
+Once the program is launched, user can click ``Open Source" at top left and then choose the folder 
+where the software project's source tree resides in the popup open directory dialog.
+Then by clicking ``Analyze" button on the right side, EasyMerge starts analyzing the selected source tree.
+
+There are five text boxes displayed on the main interface.
+Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
+All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record.
+
+User can click each item in the ``Possible Merges" list. When one item is selected, a corresponding clone set will be loaded. All files
+associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI.
+Inside the source code browser, code fragment that
 

### 2014-03-17 EasyMerge/tests/fig/fig/service.py

@@ -1,0 +1,360 @@
+from __future__ import unicode_literals
+from __future__ import absolute_import
+from .packages.docker.client import APIError
+import logging
+import re
+import os
+import sys
+from .container import Container
+
+log = logging.getLogger(__name__)
+
+
+DOCKER_CONFIG_KEYS = ['image', 'command', 'hostname', 'user', 'detach', 'stdin_open', 'tty', 'mem_limit', 'ports', 'environment', 'dns', 'volumes', 'volumes_from', 'entrypoint', 'privileged']
+DOCKER_CONFIG_HINTS = {
+    'link'      : 'links',
+    'port'      : 'ports',
+    'privilege' : 'privileged',
+    'priviliged': 'privileged',
+    'privilige' : 'privileged',
+    'volume'    : 'volumes',
+}
+
+
+class BuildError(Exception):
+    pass
+
+
+class CannotBeScaledError(Exception):
+    pass
+
+
+class ConfigError(ValueError):
+    pass
+
+
+class Service(object):
+    def __init__(self, name, client=None, project='default', links=[], **options):
+        if not re.match('^[a-zA-Z0-9]+$', name):
+            raise ConfigError('Invalid name: %s' % name)
+        if not re.match('^[a-zA-Z0-9]+$', project):
+            raise ConfigError('Invalid project: %s' % project)
+        if 'image' in options and 'build' in options:
+            raise ConfigError('Service %s has both an image and build path specified. A service can either be built to image or use an existing image, not both.' % name)
+
+        supported_options = DOCKER_CONFIG_KEYS + ['build', 'expose']
+
+        for k in options:
+            if k not in supported_options:
+                msg = "Unsupported config option for %s service: '%s'" % (name, k)
+                if k in DOCKER_CONFIG_HINTS:
+                    msg += " (did you mean '%s'?)" % DOCKER_CONFIG_HINTS[k]
+                raise ConfigError(msg)
+
+        self.name = name
+        self.client = client
+        self.project = project
+        self.links = links or []
+        self.options = options
+
+    def containers(self, stopped=False, one_off=False):
+        l = []
+        for container in self.client.containers(all=stopped):
+            name = get_container_name(container)
+            if not name or not is_valid_name(name, one_off):
+                continue
+            project, name, number = parse_name(name)
+            if project == self.project and name == self.name:
+                l.append(Container.from_ps(self.client, container))
+        return l
+
+    def start(self, **options):
+        for c in self.containers(stopped=True):
[…]

### 2014-03-17 EasyMerge/tests/fig/tests/project_test.py

@@ -1,0 +1,120 @@
+from __future__ import unicode_literals
+from fig.project import Project, ConfigurationError
+from .testcases import DockerClientTestCase
+
+
+class ProjectTest(DockerClientTestCase):
+    def test_from_dict(self):
+        project = Project.from_dicts('figtest', [
+            {
+                'name': 'web',
+                'image': 'ubuntu'
+            },
+            {
+                'name': 'db',
+                'image': 'ubuntu'
+            }
+        ], self.client)
+        self.assertEqual(len(project.services), 2)
+        self.assertEqual(project.get_service('web').name, 'web')
+        self.assertEqual(project.get_service('web').options['image'], 'ubuntu')
+        self.assertEqual(project.get_service('db').name, 'db')
+        self.assertEqual(project.get_service('db').options['image'], 'ubuntu')
+
+    def test_from_dict_sorts_in_dependency_order(self):
+        project = Project.from_dicts('figtest', [
+            {
+                'name': 'web',
+                'image': 'ubuntu',
+                'links': ['db'],
+            },
+            {
+                'name': 'db',
+                'image': 'ubuntu'
+            }
+        ], self.client)
+
+        self.assertEqual(project.services[0].name, 'db')
+        self.assertEqual(project.services[1].name, 'web')
+
+    def test_from_config(self):
+        project = Project.from_config('figtest', {
+            'web': {
+                'image': 'ubuntu',
+            },
+            'db': {
+                'image': 'ubuntu',
+            },
+        }, self.client)
+        self.assertEqual(len(project.services), 2)
+        self.assertEqual(project.get_service('web').name, 'web')
+        self.assertEqual(project.get_service('web').options['image'], 'ubuntu')
+        self.assertEqual(project.get_service('db').name, 'db')
+        self.assertEqual(project.get_service('db').options['image'], 'ubuntu')
+
+    def test_from_config_throws_error_when_not_dict(self):
+        with self.assertRaises(ConfigurationError):
+            project = Project.from_config('figtest', {
+                'web': 'ubuntu',
+            }, self.client)
+
+    def test_get_service(self):
+        web = self.create_service('web')
+        project = Project('test', [web], self.client)
+        self.assertEqual(project.get_service('web'), web)
+
+    def test_recreate_containers(self):
+        web = self.create_service('web')
+        db = self.create_service('db')
+        project = Project('test', [web, db], self.client)
+
[…]

### 2014-03-17 EasyMerge/ui/background.py

@@ -2,7 +2,9 @@ from PyQt4 import QtGui
 from tmp.dummy import Dummy
 from merger.analyzer import Analyzer
 import os
+import time
 from merger.Result import Result
+
 
 class Background(QtGui.QWidget):
     def __init__(self):
@@ -61,7 +63,34 @@ class Background(QtGui.QWidget):
         self._list.itemClicked.connect(self.listClicked)
 
     def log(self, text):
+        now = time.strftime('%c')
+        text = '[' + now + '] - \n    ' + text
         self._log.insertPlainText(text + '\n')
+        f = open('log.txt', 'a+')
+        f.write(text + '\n')
+        f.close()
+
+
+    def populateEval(self, sets, number):
+        #Populate evaluation information for one clone set
+        #Now only generate as a dummy
+        dummy  = 'Mergeable ' + str(number) + ' evaluation:\n'
+        counter = 1
+        for key in sets:
+            dummy += 'File ' + str(counter) + ': ' + key[0] + '\n'
+            counter += 1
+
+        dummy += 'File 1 package: beets > util > confit\n'
+        dummy += 'File 2 package: beets > ui > migrate\n'
+        dummy += 'External class reference: 2\n'
+        dummy += 'External function reference: 2\n'
+        dummy += 'Extra parameters: 2\n'
+        dummy += 'Clone length: 30 lines\n'
+        dummy += 'Merge is somewhat recommended\n'
+
+        self._eval.clear()
+        self._eval.insertPlainText(dummy)
+        return dummy
 
     def openClicked(self):
         sender = self.sender()
@@ -88,7 +117,7 @@ class Background(QtGui.QWidget):
         counter = 1
         for set in sets:
             item = QtGui.QListWidgetItem('Merge ' + str(counter))
-            item.setForeground(QtGui.QColor('red'))
+            item.setForeground(QtGui.QColor('green'))
             self._list.addItem(item)
             counter += 1
 
@@ -111,16 +140,31 @@ class Background(QtGui.QWidget):
         browser = QtGui.QTextBrowser(self)
         f = open(title)
         lines = f.readlines()
-        counter = 0
+        f.close()
+        counter = 1
         for line in lines:
             indent = ''
             for i in range(0, 6 - len(str(counter))):
                 indent += ' '
             indent += str(counter) + ':    '
+
+            if counter == start + 1:
+                browser.insertHtml('###REMOVE CODE BELOW###')
+                browser.insertPlainText('\n')
+            elif counter == end + 2:
[…]

### 2014-03-17 paper/paper.tex
paper updates

@@
 User can click each item in the ``Possible Merges" list. When one item is selected, a corresponding clone set will be loaded. All files
-associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI.
-Inside the source code browser, code fragment that
+associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI, where we can navigate to the
+corresponding source file by clicking each tab.
+Inside the source code browser, code that will be removed after merging is between ``\#\#\#REMOVE\_CODE\_BELOW\#\#\#"
+and ``\#\#\#REMOVE\_CODE\_ABOVE\#\#\#". And the replacement code is between ``\#\#\#REPLACE\_WITH\#\#\#"
+and ``\#\#\#REPLACE\_END\#\#\#".
+
+On the bottom part of the screen, the ``Log" and ``Evaluation" windows are placed on the left. The ``Log" window keeps track of
+program running and debugging information. Moreover, its content will also be dumped to ``log.txt" file in EasyMerge's main folder for
+book keeping purpose and developers may use it to help with writing change log. The ``Evaluation" window displays evaluation metrics
+for each code clone set, and will tell user whether we recommend a code merge for the set or not.
+
+Last but not least, the ``Extracted Method" box display the extracted method we generated as a helper function all code replacement 
+in original source code files are calling. After reviewing all information and recommendation we provide, a user can perform the code refactoring for
+a certain set by clicking ``Merge" button on bottom left. 
+EasyMerge in turn will rewrite the source files and move the generated helper to our specific accessible file in back-end.
+And all merging done in current session can be redone by clicking ``Unmerge" button if
+the user performed an unwanted merge.
 
@@
 \section{Experimental Results}
+All experiments are done on a desktop computer. The testing machine has an AMD FX 3.5GHz 6 cores CPU, 16 GB of memory,
+128 KB L1 cache, 6 MB L2 cache (1 MB per core), and 8 MB shared L3 cache. The machine runs Ubuntu Desktop 12.04, Python
+2.7.5 and has all related packages installed. For test cases, we have three popular Python powered open source projects found on GitHub of different sizes and covers
+different usage domains.
+They are ``Beets - the media library management system for obsessive-compulsive music geeks", ``Fig - fast, isolated development environments using Docker",
+and ``Wagtail - a new Django content management system".
 

### 2014-03-17 EasyMerge/clonedigger/clone_detection_algorithm.py
first final ver

@@ -199,21 +199,26 @@ def findDuplicateCode(source_files, report):
             pair_sequences = pairs_sequences.pop()
             def all_pairsubsequences_size_n_threshold(n):
                 lr = []
+                sizing = []
                 for first in range(0, pair_sequences.getLength()-n+1):
                     new_pair_sequences = pair_sequences.subSequence(first, n)
                     size = new_pair_sequences.getMaxCoveredLineNumbersCount()
                     if size >= arguments.size_threshold:
                         lr.append((new_pair_sequences, first))
-                return lr
+                        sizing.append(size)
+                return lr,sizing
             n = pair_sequences.getLength() + 1
             while 1:
                 n-=1
                 if n == 0:
                     break
-                new_pairs_sequences = all_pairsubsequences_size_n_threshold(n)
+                new_pairs_sequences, sizing = all_pairsubsequences_size_n_threshold(n)
                 for (candidate_sequence, first) in new_pairs_sequences:             
                     distance = candidate_sequence.calcDistance()
-                    if (distance < arguments.distance_threshold):
+                    cur_size = sizing[new_pairs_sequences.index((candidate_sequence, first))]
+                    #if (distance < arguments.distance_threshold) and distance>cur_size:
+                    #    print "Filtered : D="+str(distance)+", S="+str(cur_size)
+                    if (distance < arguments.distance_threshold) and (distance<=cur_size):
                         r.append(candidate_sequence)
                         if first > 0:
                             pairs_sequences.append(pair_sequences.subSequence(0, first-1))

### 2014-03-17 EasyMerge/clonedigger/clonedigger.py

@@ -33,7 +33,7 @@ import arguments
 import html_report
 import debug
 
-def main(cmdline, dir=None, custom_distance_threshold=None):
+def main(cmdline, dir=None, custom_distance_threshold=None, custom_size_threshold=None):
    
     cmdline.add_option('-l', '--language', dest='language',
                        type='choice', choices=['python', 'java', 'lua', 'javascript', 'js'],
@@ -135,6 +135,9 @@ def main(cmdline, dir=None, custom_distance_threshold=None):
         
     if custom_distance_threshold:
         arguments.distance_threshold = custom_distance_threshold
+        
+    if custom_size_threshold:
+        arguments.size_threshold = custom_size_threshold
     
     report.startTimer('Construction of AST')
     

### 2014-03-17 EasyMerge/merger/Result.py

@@ -15,6 +15,26 @@ class Result:
         self._tag.append(tag)
     def add_caller(self, tag, caller):
         self._caller[tag] = caller
+
+    def check_diff_pak(self):
+        
+        def in_diff_pak(s1,s2):
+            s1 = s1.split("/")[:-1]
+            s2 = s2.split("/")[:-1]
+            if len(s1)<len(s2):
+                s2 = s2[:len(s1)]
+            elif len(s1)>len(s2):
+                s1 = s1[:len(s2)]                
+            return not s1==s2
+        
+        tags = self._caller.keys()
+        fn1 = tags[0][0]
+        self.diff_pak = False
+        for i in tags[1:]:
+            if in_diff_pak(fn1, i[0]):
+                self.diff_pak = True
+                break
+
     def get_code(self):
         return self._code
     def get_caller(self):
@@ -26,4 +46,5 @@ class Result:
         for i in self._caller:
             print i,":"
             print self._caller[i]
+        print "External:", self.external
 

### 2014-03-17 EasyMerge/merger/clone_refiner.py

@@ -1,0 +1,395 @@
+'''
+Created on Mar 17, 2014
+
+@author: h7qin
+'''
+
+from optparse import OptionParser
+import clonedigger.clonedigger as digger
+import clonedigger.anti_unification as anti_unification
+from clonedigger.abstract_syntax_tree import StatementSequence
+from clonedigger.debug import AST
+
+stat = []
+
+def sortDuplicates(duplicates):
+    def f(a,b):
+        return cmp(b.getMaxCoveredLineNumbersCount(), a.getMaxCoveredLineNumbersCount())
+    duplicates.sort(f)
+
+def tagging(stmt_seq):
+    tag = []
+    tag.append(stmt_seq.getSourceFile().getFileName())
+    tag.append(min(stmt_seq.getCoveredLineNumbers()))
+    tag.append(max(stmt_seq.getCoveredLineNumbers()))
+    return tuple(tag)
+
+def getInfoFromSet(dSet, pair = False):
+    numOfSet = len(dSet)
+    if pair:
+        dupInCluster = 2
+        
+        indepLine = {}
+        for i in dSet:
+            for j in (0,1):
+                dup = i[j]
+                srcName = dup.getSourceFile().getFileName()
+                for n in dup.getCoveredLineNumbers():
+                    tag = srcName+"@"+str(n)
+                    if tag in indepLine:
+                        indepLine[tag] += 1
+                    else:
+                        indepLine[tag] = 1
+        
+        lineCovered = len(indepLine)
+        lineAvgRep = float(sum(indepLine.values()))/float(len(indepLine))
+                    
+    else:
+        totalDup = 0
+        for i in dSet:
+            totalDup+= len(i)
+        dupInCluster = float(totalDup)/float(numOfSet)
+        
+        indepLine = {}
+        for i in dSet:
+            for dup in i: 
+                srcName = dup.getSourceFile().getFileName()
+                for n in dup.getCoveredLineNumbers():
+                    tag = srcName+"@"+str(n)
+                    if tag in indepLine:
+                        indepLine[tag] += 1
+                    else:
+                        indepLine[tag] = 1
+        
+        lineCovered = len(indepLine)
+        lineAvgRep = float(sum(indepLine.values()))/float(len(indepLine))
+        
+    return numOfSet, dupInCluster, lineCovered, lineAvgRep
+
+def mergeStmtSeqs(duplicates):
+    tag_dict = {}
+    duplicate_set = []
[…]

### 2014-03-17 EasyMerge/merger/evaluation.py

@@ -1,0 +1,45 @@
+'''
+Created on Mar 17, 2014
+
+@author: h7qin
+'''
+import os
+
+def getTotalSourceLineNumbers(dir):
+    def walk(dirname):
+        for dirpath, dirs, files in os.walk(dir):
+            dirs[:] = [d for d in dirs]
+            files[:] = [f for f in files]
+            yield (dirpath, dirs, files)
+    def getLineNumber(filename):
+        total_file+=1
+        f = open(filename, "r")
+        lines = f.readlines()
+        return len(lines)
+    
+    total_num = 0
+    total_file = 0
+    for dirpath, dirnames, filenames in walk(dir):
+        #print dirpath, dirnames, filenames
+        for f in filenames:
+            if f[-3:]!=".py":
+                continue
+            filename = os.path.join(dirpath, f)
+            linenum = getLineNumber(filename)
+            total_num += linenum
+    print total_num,"lines in total"
+    print total_file,"files in total"
+    return total_num, total_file
+
+
+
+def getOtherStats(dir, distance_threshold, size_threshold):
+    import clone_refiner
+    stat = clone_refiner.main(dir, distance_threshold, size_threshold, True)
+    for i in stat:
+        print i
+    
+if __name__ == '__main__':
+    dir_name = "../tests/beets"
+    total_num, total_file = getTotalSourceLineNumbers(dir_name)
+    getOtherStats(dir_name, 10, 4)

### 2014-03-17 EasyMerge/merger/merger.py

@@ -16,11 +16,17 @@ import type1_0_dealer as type1_dealer
 import type3_dealer
 
 mergeResults = []
-
-def sortDuplicates(duplicates):
-    def f(a,b):
-        return cmp(b.getMaxCoveredLineNumbersCount(), a.getMaxCoveredLineNumbersCount())
-    duplicates.sort(f)
+stat ={"Merged":0, 
+       "MergedIdentical":0, 
+       "MergedDiff":0, 
+       "MergedDist":0,
+       "External": (0, 0), 
+       "DiffDef":0, 
+       "ErrorDef":0,
+       "DiffStmt":0,
+       "ErrorStmt":0,
+       "DiffPak":0,
+       "Reduction":[]}
 
 def tagging(stmt_seq):
     tag = []
@@ -28,281 +34,6 @@ def tagging(stmt_seq):
     tag.append(min(stmt_seq.getCoveredLineNumbers()))
     tag.append(max(stmt_seq.getCoveredLineNumbers()))
     return tuple(tag)
-
-def mergeStmtSeqs(duplicates):
-    print "Found", len(duplicates), "Pairs"
-    tag_dict = {}
-    duplicate_set = []
-    for i in duplicates:
-        clone_id = len(duplicate_set)
-        tag = [(),()]
-        for j in [0,1]:
-            tag[j] = tagging(i[j])
-        if not tag[0] in tag_dict and not tag[1] in tag_dict:
-            duplicate_set.append([i[0],i[1]])
-            tag_dict[tag[0]] = clone_id
-            tag_dict[tag[1]] = clone_id
-        elif tag[0] in tag_dict and not tag[1] in tag_dict:
-            duplicate_set[tag_dict[tag[0]]].append(i[1])
-            tag_dict[tag[1]] = tag_dict[tag[0]]
-        elif tag[1] in tag_dict and not tag[0] in tag_dict:
-            duplicate_set[tag_dict[tag[1]]].append(i[0])
-            tag_dict[tag[0]] = tag_dict[tag[1]]
-        else:
-            pass
-    print "Merged into",len(duplicate_set),"Sets"
-    return duplicate_set
-
-def dup_class_fliter(duplicate_set):
-    filter = ["Class", "Import", "From","Return"]
-    rm_cluster = []
-    info = {0:[]}
-    for cluster in duplicate_set:
-        for id in range(len(cluster)):
-            seq = cluster[id]
-            rm_stmt = []
-            for ast in seq:
[…]

### 2014-03-17 EasyMerge/merger/type1_0_dealer.py

@@ -996,6 +996,7 @@ def generateNewCode(id, source, lines, src_ast, tag, output=sys.stdout):
     merged.write_head_line(up.vars)
     merged.write_return_line(up.return_vars)
     merged.get_caller()
+    
     return merged
 
 
@@ -1024,6 +1025,8 @@ def mergeDiffResults(merged_list):
         i.rewrite_head_line(paramList)
         i.rewrite_return_line(returnList)
         i.reget_caller(paramList, returnList)
+        i.param = paramList
+        i.return_vars = returnList
     
     return merged_list
     

### 2014-03-17 EasyMerge/merger/type3_dealer.py

@@ -1053,35 +1053,6 @@ def generateNewCode(id, source, lines, src_ast, tag, output=sys.stdout):
     #print up.vars
     return merged
 
-
-'''def mergeDiffResults(merged_list):
-    def mergeSet(setList):
-        d = {}
-        for i in setList:
-            for j in i:
-                if j in d:
-                    d[j] += 1
-                else:
-                    d[j] = 1
-        return d
-    
-    paramList = []
-    returnList = []
-    
-    for i in merged_list:
-        paramList.append(i.param)
-        returnList.append(i.return_vars)
-    
-    paramList = mergeSet(paramList).keys()
-    returnList = mergeSet(returnList).keys()
-    
-    for i in merged_list:
-        i.rewrite_head_line(paramList)
-        i.rewrite_return_line(returnList)
-        i.reget_caller(paramList, returnList)
-    
-    return merged_list'''
-
 def checkMergable(merged_list):
     mergable = True
     for merge in merged_list[1:]:
@@ -1188,6 +1159,10 @@ def generateCommonCode(merged_list):
         merge.rewrite_head_line(common_param)
         merge.rewrite_return_line(common_ret)
         merge.reget_caller(new_caller[i], new_receiver[i])
+        
+        merge.param = common_param
+        merge.return_vars = common_ret
+        
         #merge.output()
         merged_list[i] = merge
     

### 2014-03-17 paper/paper.tex
updates

@@
 
-There are five text boxes displayed on the main interface.
+There are five window boxes displayed on the main interface.
 Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
@@
 And all merging done in current session can be redone by clicking ``Unmerge" button if
-the user performed an unwanted merge.
+the user performed an unwanted merge for a certain set.
 

### 2014-03-17 EasyMerge/ui/background.py

@@ -92,6 +92,11 @@ class Background(QtGui.QWidget):
         self._eval.insertPlainText(dummy)
         return dummy
 
+    def warn(self, msg):
+        box = QtGui.QMessageBox(self)
+        box.setText(msg)
+        box.exec_()
+
     def openClicked(self):
         sender = self.sender()
         self._path = str(QtGui.QFileDialog.getExistingDirectory(sender, 'Select source code directory'))
@@ -100,9 +105,7 @@ class Background(QtGui.QWidget):
 
     def analyzeClicked(self):
         if self._path == '':
-            msg = QtGui.QMessageBox(self)
-            msg.setText('Please select source code directory first by clicking [Open Source]')
-            msg.exec_()
+            self.warn('Please select source code directory first by clicking [Open Source]')
         else:
             #analyze
             self.log('Start running CloneDigger...')
@@ -189,8 +192,41 @@ class Background(QtGui.QWidget):
 
 
     def mergeClicked(self):
+        item = self._list.currentItem()
+        index = self._list.currentRow()
+        sets = self._sets[index].get_caller()
+        redness = item.foreground().color().red()
+        if redness == 0:
+            #green
+            item.setForeground(QtGui.QColor('red'))
+            info = 'Files:\n'
+            for key in sets:
+                info += key[0] + '\n'
+            info += 'merged.\n'
+            self.log(info)
+        else:
+            #red
+            self.warn('Item has already been merged!')
+
+        color = str(item.foreground().color().red())
+        print color
         print 'mergining...'
 
     def unmergeClicked(self):
+        item = self._list.currentItem()
+        index = self._list.currentRow()
+        sets = self._sets[index].get_caller()
+        redness = item.foreground().color().red()
+        if redness == 0:
+            #green
+            self.warn('Item has not been merged yet!')
+        else:
+            #red
+            item.setForeground(QtGui.QColor('green'))
+            info = 'Files:\n'
+            for key in sets:
+                info += key[0] + '\n'
+            info == 'unmerged.\n'
+            self.log(info)
         print 'unmerging...'
 

### 2014-03-17 EasyMerge/tests/Untitled Folder/autotag/__init__.py
remove unwanted code

@@ -1,244 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Facilities for automatically determining files' correct metadata.
-"""
-import os
-import logging
-import re
-
-from beets import library, mediafile, config
-from beets.util import sorted_walk, ancestry, displayable_path
-
-# Parts of external interface.
-from .hooks import AlbumInfo, TrackInfo, AlbumMatch, TrackMatch
-from .match import tag_item, tag_album
-from .match import recommendation
-
-# Global logger.
-log = logging.getLogger('beets')
-
-# Constants for directory walker.
-MULTIDISC_MARKERS = (r'dis[ck]', r'cd')
-MULTIDISC_PAT_FMT = r'^(.*%s[\W_]*)\d'
-
-
-# Additional utilities for the main interface.
-
-def albums_in_dir(path):
-    """Recursively searches the given directory and returns an iterable
-    of (paths, items) where paths is a list of directories and items is
-    a list of Items that is probably an album. Specifically, any folder
-    containing any media files is an album.
-    """
-    collapse_pat = collapse_paths = collapse_items = None
-
-    for root, dirs, files in sorted_walk(path,
-                                         ignore=config['ignore'].as_str_seq(),
-                                         logger=log):
-        # Get a list of items in the directory.
-        items = []
-        for filename in files:
-            try:
-                i = library.Item.from_path(os.path.join(root, filename))
-            except mediafile.FileTypeError:
-                pass
-            except mediafile.UnreadableFileError:
-                log.warn(u'unreadable file: {0}'.format(
-                    displayable_path(filename))
-                )
-            else:
-                items.append(i)
-
-        # If we're currently collapsing the constituent directories in a
-        # multi-disc album, check whether we should continue collapsing
-        # and add the current directory. If so, just add the directory
-        # and move on to the next directory. If not, stop collapsing.
-        if collapse_paths:
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/autotag/hooks.py

@@ -1,545 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Glue between metadata sources and the matching logic."""
-import logging
-from collections import namedtuple
-import re
-
-from beets import plugins
-from beets import config
-from beets.autotag import mb
-from beets.util import levenshtein
-from unidecode import unidecode
-
-log = logging.getLogger('beets')
-
-
-# Classes used to represent candidate options.
-
-class AlbumInfo(object):
-    """Describes a canonical release that may be used to match a release
-    in the library. Consists of these data members:
-
-    - ``album``: the release title
-    - ``album_id``: MusicBrainz ID; UUID fragment only
-    - ``artist``: name of the release's primary artist
-    - ``artist_id``
-    - ``tracks``: list of TrackInfo objects making up the release
-    - ``asin``: Amazon ASIN
-    - ``albumtype``: string describing the kind of release
-    - ``va``: boolean: whether the release has "various artists"
-    - ``year``: release year
-    - ``month``: release month
-    - ``day``: release day
-    - ``label``: music label responsible for the release
-    - ``mediums``: the number of discs in this release
-    - ``artist_sort``: name of the release's artist for sorting
-    - ``releasegroup_id``: MBID for the album's release group
-    - ``catalognum``: the label's catalog number for the release
-    - ``script``: character set used for metadata
-    - ``language``: human language of the metadata
-    - ``country``: the release country
-    - ``albumstatus``: MusicBrainz release status (Official, etc.)
-    - ``media``: delivery mechanism (Vinyl, etc.)
-    - ``albumdisambig``: MusicBrainz release disambiguation comment
-    - ``artist_credit``: Release-specific artist name
-    - ``data_source``: The original data source (MusicBrainz, Discogs, etc.)
-    - ``data_url``: The data source release URL.
-
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/autotag/match.py

@@ -1,456 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Matches existing metadata with canonical information to identify
-releases and tracks.
-"""
-from __future__ import division
-
-import datetime
-import logging
-import re
-from munkres import Munkres
-
-from beets import plugins
-from beets import config
-from beets.util import plurality
-from beets.util.enumeration import enum
-from beets.autotag import hooks
-
-# Recommendation enumeration.
-recommendation = enum('none', 'low', 'medium', 'strong', name='recommendation')
-
-# Artist signals that indicate "various artists". These are used at the
-# album level to determine whether a given release is likely a VA
-# release and also on the track level to to remove the penalty for
-# differing artists.
-VA_ARTISTS = (u'', u'various artists', u'various', u'va', u'unknown')
-
-# Global logger.
-log = logging.getLogger('beets')
-
-
-# Primary matching functionality.
-
-def current_metadata(items):
-    """Extract the likely current metadata for an album given a list of its
-    items. Return two dictionaries:
-     - The most common value for each field.
-     - Whether each field's value was unanimous (values are booleans).
-    """
-    assert items  # Must be nonempty.
-
-    likelies = {}
-    consensus = {}
-    fields = ['artist', 'album', 'albumartist', 'year', 'disctotal',
-              'mb_albumid', 'label', 'catalognum', 'country', 'media',
-              'albumdisambig']
-    for key in fields:
-        values = [getattr(item, key) for item in items if item]
-        likelies[key], freq = plurality(values)
-        consensus[key] = (freq == len(values))
-
-    # If there's an album artist consensus, use this for the artist.
-    if consensus['albumartist'] and likelies['albumartist']:
-        likelies['artist'] = likelies['albumartist']
-
-    return likelies, consensus
-
-def assign_items(items, tracks):
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/autotag/mb.py

@@ -1,397 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Searches for albums in the MusicBrainz database.
-"""
-import logging
-import musicbrainzngs
-import re
-import traceback
-from urlparse import urljoin
-
-import beets.autotag.hooks
-import beets
-from beets import util
-from beets import config
-
-SEARCH_LIMIT = 5
-VARIOUS_ARTISTS_ID = '89ad4ac3-39f7-470e-963a-56509c546377'
-BASE_URL = 'http://musicbrainz.org/'
-
-musicbrainzngs.set_useragent('beets', beets.__version__,
-                             'http://beets.radbox.org/')
-
-class MusicBrainzAPIError(util.HumanReadableException):
-    """An error while talking to MusicBrainz. The `query` field is the
-    parameter to the action and may have any type.
-    """
-    def __init__(self, reason, verb, query, tb=None):
-        self.query = query
-        super(MusicBrainzAPIError, self).__init__(reason, verb, tb)
-
-    def get_message(self):
-        return u'"{0}" in {1} with query {2}'.format(
-            self._reasonstr(), self.verb, repr(self.query)
-        )
-
-log = logging.getLogger('beets')
-
-RELEASE_INCLUDES = ['artists', 'media', 'recordings', 'release-groups',
-                    'labels', 'artist-credits', 'aliases']
-TRACK_INCLUDES = ['artists', 'aliases']
-
-def track_url(trackid):
-    return urljoin(BASE_URL, 'recording/' + trackid)
-
-def album_url(albumid):
-    return urljoin(BASE_URL, 'release/' + albumid)
-
-def configure():
-    """Set up the python-musicbrainz-ngs module according to settings
-    from the beets configuration. This should be called at startup.
-    """
-    musicbrainzngs.set_hostname(config['musicbrainz']['host'].get(unicode))
-    musicbrainzngs.set_rate_limit(
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/dbcore/__init__.py

@@ -1,20 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""DBCore is an abstract database package that forms the basis for beets'
-Library.
-"""
-from .db import Model, Database
-from .query import Query, FieldQuery, MatchQuery, AndQuery, OrQuery
-from .types import Type

### 2014-03-17 EasyMerge/tests/Untitled Folder/dbcore/db.py

@@ -1,726 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""The central Model and Database constructs for DBCore.
-"""
-import time
-import os
-from collections import defaultdict
-import threading
-import sqlite3
-import contextlib
-
-import beets
-from beets.util.functemplate import Template
-from .query import MatchQuery
-
-
-
-# Abstract base for model classes.
-
-
-class Model(object):
-    """An abstract object representing an object in the database. Model
-    objects act like dictionaries (i.e., the allow subscript access like
-    ``obj['field']``). The same field set is available via attribute
-    access as a shortcut (i.e., ``obj.field``). Three kinds of attributes are
-    available:
-
-    * **Fixed attributes** come from a predetermined list of field
-      names. These fields correspond to SQLite table columns and are
-      thus fast to read, write, and query.
-    * **Flexible attributes** are free-form and do not need to be listed
-      ahead of time.
-    * **Computed attributes** are read-only fields computed by a getter
-      function provided by a plugin.
-
-    Access to all three field types is uniform: ``obj.field`` works the
-    same regardless of whether ``field`` is fixed, flexible, or
-    computed.
-
-    Model objects can optionally be associated with a `Library` object,
-    in which case they can be loaded and stored from the database. Dirty
-    flags are used to track which fields need to be stored.
-    """
-
-    # Abstract components (to be provided by subclasses).
-
-    _table = None
-    """The main SQLite table name.
-    """
-
-    _flex_table = None
-    """The flex field SQLite table name.
-    """
-
-    _fields = {}
-    """A mapping indicating available "fixed" fields on this type. The
-    keys are field names and the values are Type objects.
-    """
-
-    _bytes_keys = ()
-    """Keys whose values should be stored as raw bytes blobs rather than
-    strings.
-    """
-
-    _search_fields = ()
-    """The fields that should be queried by default by unqualified query
-    terms.
-    """
-
-    @classmethod
-    def _getters(cls):
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/dbcore/query.py

@@ -1,494 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""The Query type hierarchy for DBCore.
-"""
-import re
-from beets import util
-from datetime import datetime, timedelta
-
-
-class Query(object):
-    """An abstract class representing a query into the item database.
-    """
-    def clause(self):
-        """Generate an SQLite expression implementing the query.
-        Return a clause string, a sequence of substitution values for
-        the clause, and a Query object representing the "remainder"
-        Returns (clause, subvals) where clause is a valid sqlite
-        WHERE clause implementing the query and subvals is a list of
-        items to be substituted for ?s in the clause.
-        """
-        return None, ()
-
-    def match(self, item):
-        """Check whether this query matches a given Item. Can be used to
-        perform queries on arbitrary sets of Items.
-        """
-        raise NotImplementedError
-
-
-class FieldQuery(Query):
-    """An abstract query that searches in a specific field for a
-    pattern. Subclasses must provide a `value_match` class method, which
-    determines whether a certain pattern string matches a certain value
-    string. Subclasses may also provide `col_clause` to implement the
-    same matching functionality in SQLite.
-    """
-    def __init__(self, field, pattern, fast=True):
-        self.field = field
-        self.pattern = pattern
-        self.fast = fast
-
-    def col_clause(self):
-        return None, ()
-
-    def clause(self):
-        if self.fast:
-            return self.col_clause()
-        else:
-            # Matching a flexattr. This is a slow query.
-            return None, ()
-
-    @classmethod
-    def value_match(cls, pattern, value):
-        """Determine whether the value matches the pattern. Both
-        arguments are strings.
-        """
-        raise NotImplementedError()
-
-    def match(self, item):
-        return self.value_match(self.pattern, item.get(self.field))
-
-
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/dbcore/types.py

@@ -1,140 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Representation of type information for DBCore model fields.
-"""
-from . import query
-from beets.util import str2bool
-
-
-
-# Abstract base.
-
-
-class Type(object):
-    """An object encapsulating the type of a model field. Includes
-    information about how to store the value in the database, query,
-    format, and parse a given field.
-    """
-
-    sql = None
-    """The SQLite column type for the value.
-    """
-
-    query = None
-    """The `Query` subclass to be used when querying the field.
-    """
-
-    def format(self, value):
-        """Given a value of this type, produce a Unicode string
-        representing the value. This is used in template evaluation.
-        """
-        raise NotImplementedError()
-
-    def parse(self, string):
-        """Parse a (possibly human-written) string and return the
-        indicated value of this type.
-        """
-        raise NotImplementedError()
-
-
-
-# Reusable types.
-
-
-class Integer(Type):
-    """A basic integer type.
-    """
-    sql = u'INTEGER'
-    query = query.NumericQuery
-
-    def format(self, value):
-        return unicode(value or 0)
-
-    def parse(self, string):
-        try:
-            return int(string)
-        except ValueError:
-            return 0
-
-
-class PaddedInt(Integer):
-    """An integer field that is formatted with a given number of digits,
-    padded with zeroes.
-    """
-    def __init__(self, digits):
-        self.digits = digits
-
-    def format(self, value):
-        return u'{0:0{1}d}'.format(value or 0, self.digits)
-
-
-class ScaledInt(Integer):
-    """An integer whose formatting operation scales the number by a
-    constant and adds a suffix. Good for units with large magnitudes.
-    """
-    def __init__(self, unit, suffix=u''):
-        self.unit = unit
-        self.suffix = suffix
-
-    def format(self, value):
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/ui/__init__.py

@@ -1,973 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""This module contains all of the core logic for beets' command-line
-interface. To invoke the CLI, just call beets.ui.main(). The actual
-CLI commands are implemented in the ui.commands module.
-"""
-from __future__ import print_function
-
-import locale
-import optparse
-import textwrap
-import sys
-from difflib import SequenceMatcher
-import logging
-import sqlite3
-import errno
-import re
-import struct
-import traceback
-
-from beets import library
-from beets import plugins
-from beets import util
-from beets.util.functemplate import Template
-from beets import config
-from beets.util import confit
-from beets.autotag import mb
-
-
-# On Windows platforms, use colorama to support "ANSI" terminal colors.
-
-if sys.platform == 'win32':
-    try:
-        import colorama
-    except ImportError:
-        pass
-    else:
-        colorama.init()
-
-
-
-# Constants.
-
-
-PF_KEY_QUERIES = {
-    'comp': 'comp:true',
-    'singleton': 'singleton:true',
-}
-
-# UI exception. Commands should throw this in order to display
-# nonrecoverable errors to the user.
-class UserError(Exception):
-    pass
-
-# Main logger.
-log = logging.getLogger('beets')
-
-
-
-# Utilities.
-
-
-def _encoding():
-    """Tries to guess the encoding used by the terminal."""
-    # Configured override?
-    encoding = config['terminal_encoding'].get()
-    if encoding:
-        return encoding
-
-    # Determine from locale settings.
-    try:
-        return locale.getdefaultlocale()[1] or 'utf8'
-    except ValueError:
-        # Invalid locale environment variable setting. To avoid
-        # failing entirely for no good reason, assume UTF-8.
-        return 'utf8'
-
-
-def decargs(arglist):
-    """Given a list of command-line argument bytestrings, attempts to
-    decode them to Unicode strings.
-    """
-    return [s.decode(_encoding()) for s in arglist]
-
-
-def print_(*strings):
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/ui/commands.py

@@ -1,1405 +1,0 @@
-# This file is part of beets.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""This module provides the default commands for beets' command-line
-interface.
-"""
-from __future__ import print_function
-
-import logging
-import os
-import time
-import itertools
-import codecs
-import platform
-
-import beets
-from beets import ui
-from beets.ui import print_, input_, decargs
-from beets import autotag
-from beets.autotag import recommendation
-from beets.autotag import hooks
-from beets import plugins
-from beets import importer
-from beets import util
-from beets.util import syspath, normpath, ancestry, displayable_path
-from beets.util.functemplate import Template
-from beets import library
-from beets import config
-from beets.util.confit import _package_path
-
-# Global logger.
-log = logging.getLogger('beets')
-
-# The list of default subcommands. This is populated with Subcommand
-# objects that can be fed to a SubcommandsOptionParser.
-default_commands = []
-
-
-
-# Utilities.
-
-
-def _do_query(lib, query, album, also_items=True):
-    """For commands that operate on matched items, performs a query
-    and returns a list of matching items and a list of matching
-    albums. (The latter is only nonempty when album is True.) Raises
-    a UserError if no items match. also_items controls whether, when
-    fetching albums, the associated items should be fetched also.
-    """
-    if album:
-        albums = list(lib.albums(query))
-        items = []
-        if also_items:
-            for al in albums:
-                items += al.items()
-
-    else:
-        albums = []
-        items = list(lib.items(query))
-
-    if album and not albums:
-        raise ui.UserError('No matching albums found.')
-    elif not album and not items:
-        raise ui.UserError('No matching items found.')
-
-    return items, albums
-
-
-
-# fields: Shows a list of available fields for queries and format strings.
-
-fields_cmd = ui.Subcommand('fields',
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/util/__init__.py

@@ -1,618 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Miscellaneous utility functions."""
-from __future__ import division
-
-import os
-import sys
-import re
-import shutil
-import fnmatch
-from collections import defaultdict
-import traceback
-import subprocess
-
-MAX_FILENAME_LENGTH = 200
-WINDOWS_MAGIC_PREFIX = u'\\\\?\\'
-
-class HumanReadableException(Exception):
-    """An Exception that can include a human-readable error message to
-    be logged without a traceback. Can preserve a traceback for
-    debugging purposes as well.
-
-    Has at least two fields: `reason`, the underlying exception or a
-    string describing the problem; and `verb`, the action being
-    performed during the error.
-
-    If `tb` is provided, it is a string containing a traceback for the
-    associated exception. (Note that this is not necessary in Python 3.x
-    and should be removed when we make the transition.)
-    """
-    error_kind = 'Error'  # Human-readable description of error type.
-
-    def __init__(self, reason, verb, tb=None):
-        self.reason = reason
-        self.verb = verb
-        self.tb = tb
-        super(HumanReadableException, self).__init__(self.get_message())
-
-    def _gerund(self):
-        """Generate a (likely) gerund form of the English verb.
-        """
-        if ' ' in self.verb:
-            return self.verb
-        gerund = self.verb[:-1] if self.verb.endswith('e') else self.verb
-        gerund += 'ing'
-        return gerund
-    
-    def _reasonstr(self):
-        """Get the reason as a string."""
-        if isinstance(self.reason, unicode):
-            return self.reason
-        elif isinstance(self.reason, basestring):  # Byte string.
-            return self.reason.decode('utf8', 'ignore')
-        elif hasattr(self.reason, 'strerror'):  # i.e., EnvironmentError
-            return self.reason.strerror
-        else:
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/util/artresizer.py

@@ -1,188 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Fabrice Laporte
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Abstraction layer to resize images using PIL, ImageMagick, or a
-public resizing proxy if neither is available.
-"""
-import urllib
-import subprocess
-import os
-from tempfile import NamedTemporaryFile
-import logging
-from beets import util
-
-# Resizing methods
-PIL = 1
-IMAGEMAGICK = 2
-WEBPROXY = 3
-
-PROXY_URL = 'http://images.weserv.nl/'
-
-log = logging.getLogger('beets')
-
-
-def resize_url(url, maxwidth):
-    """Return a proxied image URL that resizes the original image to
-    maxwidth (preserving aspect ratio).
-    """
-    return '{0}?{1}'.format(PROXY_URL, urllib.urlencode({
-        'url': url.replace('http://',''),
-        'w': str(maxwidth),
-    }))
-
-
-def temp_file_for(path):
-    """Return an unused filename with the same extension as the
-    specified path.
-    """
-    ext = os.path.splitext(path)[1]
-    with NamedTemporaryFile(suffix=ext, delete=False) as f:
-        return f.name
-
-
-def pil_resize(maxwidth, path_in, path_out=None):
-    """Resize using Python Imaging Library (PIL).  Return the output path
-    of resized image.
-    """
-    path_out = path_out or temp_file_for(path_in)
-    from PIL import Image
-    log.debug(u'artresizer: PIL resizing {0} to {1}'.format(
-        util.displayable_path(path_in), util.displayable_path(path_out)
-    ))
-
-    try:
-        im = Image.open(util.syspath(path_in))
-        size = maxwidth, maxwidth
-        im.thumbnail(size, Image.ANTIALIAS)
-        im.save(path_out)
-        return path_out
-    except IOError:
-        log.error(u"PIL cannot create thumbnail for '{0}'".format(
-            util.displayable_path(path_in)
-        ))
-        return path_in
-
-
-def im_resize(maxwidth, path_in, path_out=None):
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/util/confit.py

@@ -1,900 +1,0 @@
-# This file is part of Confit.
-# Copyright 2014, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Worry-free YAML configuration files.
-"""
-from __future__ import unicode_literals
-import platform
-import os
-import pkgutil
-import sys
-import yaml
-import types
-try:
-    from collections import OrderedDict
-except ImportError:
-    from ordereddict import OrderedDict
-
-UNIX_DIR_VAR = 'XDG_CONFIG_HOME'
-UNIX_DIR_FALLBACK = '~/.config'
-WINDOWS_DIR_VAR = 'APPDATA'
-WINDOWS_DIR_FALLBACK = '~\\AppData\\Roaming'
-MAC_DIR = '~/Library/Application Support'
-
-CONFIG_FILENAME = 'config.yaml'
-DEFAULT_FILENAME = 'config_default.yaml'
-ROOT_NAME = 'root'
-
-YAML_TAB_PROBLEM = "found character '\\t' that cannot start any token"
-
-
-# Utilities.
-
-PY3 = sys.version_info[0] == 3
-STRING = str if PY3 else unicode
-BASESTRING = str if PY3 else basestring
-NUMERIC_TYPES = (int, float) if PY3 else (int, float, long)
-TYPE_TYPES = (type,) if PY3 else (type, types.ClassType)
-
-def iter_first(sequence):
-    """Get the first element from an iterable or raise a ValueError if
-    the iterator generates no values.
-    """
-    it = iter(sequence)
-    try:
-        if PY3:
-            return next(it)
-        else:
-            return it.next()
-    except StopIteration:
-        raise ValueError()
-
-
-# Exceptions.
-
-class ConfigError(Exception):
-    """Base class for exceptions raised when querying a configuration.
-    """
-
-class NotFoundError(ConfigError):
-    """A requested value could not be found in the configuration trees.
-    """
-
-class ConfigTypeError(ConfigError, TypeError):
-    """The value in the configuration did not match the expected type.
-    """
-
[…]

### 2014-03-17 EasyMerge/tests/Untitled Folder/util/pipeline.py

@@ -1,454 +1,0 @@
-# This file is part of beets.
-# Copyright 2013, Adrian Sampson.
-#
-# Permission is hereby granted, free of charge, to any person obtaining
-# a copy of this software and associated documentation files (the
-# "Software"), to deal in the Software without restriction, including
-# without limitation the rights to use, copy, modify, merge, publish,
-# distribute, sublicense, and/or sell copies of the Software, and to
-# permit persons to whom the Software is furnished to do so, subject to
-# the following conditions:
-#
-# The above copyright notice and this permission notice shall be
-# included in all copies or substantial portions of the Software.
-
-"""Simple but robust implementation of generator/coroutine-based
-pipelines in Python. The pipelines may be run either sequentially
-(single-threaded) or in parallel (one thread per pipeline stage).
-
-This implementation supports pipeline bubbles (indications that the
-processing for a certain item should abort). To use them, yield the
-BUBBLE constant from any stage coroutine except the last.
-
-In the parallel case, the implementation transparently handles thread
-shutdown when the processing is complete and when a stage raises an
-exception. KeyboardInterrupts (^C) are also handled.
-
-When running a parallel pipeline, it is also possible to use
-multiple coroutines for the same pipeline stage; this lets you speed
-up a bottleneck stage by dividing its work among multiple threads.
-To do so, pass an iterable of coroutines to the Pipeline constructor
-in place of any single coroutine.
-"""
-from __future__ import print_function
-
-import Queue
-from threading import Thread, Lock
-import sys
-import types
-
-BUBBLE = '__PIPELINE_BUBBLE__'
-POISON = '__PIPELINE_POISON__'
-
-DEFAULT_QUEUE_SIZE = 16
-
-def _invalidate_queue(q, val=None, sync=True):
-    """Breaks a Queue such that it never blocks, always has size 1,
-    and has no maximum size. get()ing from the queue returns `val`,
-    which defaults to None. `sync` controls whether a lock is
-    required (because it's not reentrant!).
-    """
-    def _qsize(len=len):
-        return 1
-    def _put(item):
-        pass
-    def _get():
-        return val
-
-    if sync:
-        q.mutex.acquire()
-
-    try:
-        q.maxsize = 0
-        q._qsize = _qsize
-        q._put = _put
-        q._get = _get
-        q.not_empty.notifyAll()
-        q.not_full.notifyAll()
-
-    finally:
-        if sync:
-            q.mutex.release()
-
[…]

### 2014-03-17 EasyMerge/tests/chisel/commands/FBDisplayCommands.py

@@ -1,140 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import lldb
-import os
-import time
-
-import fblldbviewhelpers as viewHelpers
-import fblldbbase as fb
-
-def lldbcommands():
-  return [
-    FBCoreAnimationFlushCommand(),
-    FBDrawBorderCommand(),
-    FBRemoveBorderCommand(),
-    FBMaskViewCommand(),
-    FBUnmaskViewCommand(),
-    FBShowViewCommand(),
-    FBHideViewCommand(),
-  ]
-
-
-class FBDrawBorderCommand(fb.FBCommand):
-  def name(self):
-    return 'border'
-
-  def description(self):
-    return 'Draws a border around <viewOrLayer>. Color and width can be optionally provided.'
-
-  def args(self):
-    return [ fb.FBCommandArgument(arg='viewOrLayer', type='UIView/CALayer *', help='The view/layer to border.') ]
-
-  def options(self):
-    return [
-      fb.FBCommandArgument(short='-c', long='--color', arg='color', type='string', default='red', help='A color name such as \'red\', \'green\', \'magenta\', etc.'),
-      fb.FBCommandArgument(short='-w', long='--width', arg='width', type='CGFloat', default=2.0, help='Desired width of border.')
-    ]
-
-  def run(self, args, options):
-    layer = viewHelpers.convertToLayer(args[0])
-    lldb.debugger.HandleCommand('expr (void)[%s setBorderWidth:(CGFloat)%s]' % (layer, options.width))
-    lldb.debugger.HandleCommand('expr (void)[%s setBorderColor:(CGColorRef)[(id)[UIColor %sColor] CGColor]]' % (layer, options.color))
-    lldb.debugger.HandleCommand('caflush')
-
-
-class FBRemoveBorderCommand(fb.FBCommand):
-  def name(self):
-    return 'unborder'
-
-  def description(self):
-    return 'Removes border around <viewOrLayer>.'
-
-  def args(self):
-    return [ fb.FBCommandArgument(arg='viewOrLayer', type='UIView/CALayer *', help='The view/layer to unborder.') ]
-
-  def run(self, args, options):
[…]

### 2014-03-17 EasyMerge/tests/chisel/commands/FBFindCommands.py

@@ -1,155 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import os
-import re
-
-import lldb
-import fblldbbase as fb
-import fblldbviewcontrollerhelpers as vcHelpers
-import fblldbobjcruntimehelpers as objc
-
-def lldbcommands():
-  return [
-    FBFindViewControllerCommand(),
-    FBFindViewCommand(),
-    FBFindViewByAccessibilityLabelCommand(),
-    FBTapLoggerCommand(),
-  ]
-
-class FBFindViewControllerCommand(fb.FBCommand):
-  def name(self):
-    return 'fvc'
-
-  def description(self):
-    return 'Find the view controllers whose class names match classNameRegex and puts the address of first on the clipboard.'
-
-  def options(self):
-    return [
-      fb.FBCommandArgument(short='-n', long='--name', arg='classNameRegex', type='string', help='The view-controller-class regex to search the view controller hierarchy for.'),
-      fb.FBCommandArgument(short='-v', long='--view', arg='view', type='UIView', help='This function will print the View Controller that owns this view.')
-    ]
-
-  def run(self, arguments, options):
-    if options.classNameRegex and options.view:
-      print("Do not set both the --name and --view flags")
-    elif options.view:
-      self.findOwningViewController(options.view)
-    else:
-      output = vcHelpers.viewControllerRecursiveDescription('(id)[[UIWindow keyWindow] rootViewController]')
-      searchString = options.classNameRegex if options.classNameRegex else arguments[0]
-      printMatchesInViewOutputStringAndCopyFirstToClipboard(searchString, output)
-
-  def findOwningViewController(self, object):
-    while object:
-      if self.isViewController(object):
-        description = fb.evaluateExpressionValue(object).GetObjectDescription()
-        print("Found the owning view controller.\n{}".format(description))
-        cmd = 'echo {} | tr -d "\n" | pbcopy'.format(object)
-        os.system(cmd)
-        return
-      else:
-        object = self.nextResponder(object)
[…]

### 2014-03-17 EasyMerge/tests/chisel/commands/FBPrintCommands.py

@@ -1,244 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import os
-import re
-
-import lldb
-import fblldbbase as fb
-import fblldbviewcontrollerhelpers as vcHelpers
-import fblldbviewhelpers as viewHelpers
-
-def lldbcommands():
-  return [
-    FBPrintViewHierarchyCommand(),
-    FBPrintCoreAnimationTree(),
-    FBPrintViewControllerHierarchyCommand(),
-    FBPrintIsExecutingInAnimationBlockCommand(),
-    FBPrintInheritanceHierarchy(),
-    FBPrintUpwardResponderChain(),
-    FBPrintOnscreenTableView(),
-    FBPrintOnscreenTableViewCells(),
-    FBPrintInternals(),
-    FBPrintInstanceVariable(),
-  ]
-
-class FBPrintViewHierarchyCommand(fb.FBCommand):
-  def name(self):
-    return 'pviews'
-
-  def description(self):
-    return 'Print the recursion description of <aView>.'
-
-  def options(self):
-    return [ fb.FBCommandArgument(short='-u', long='--up', arg='upwards', boolean=True, default=False, help='Print only the hierarchy directly above the view, up to its window.') ]
-
-  def args(self):
-    return [ fb.FBCommandArgument(arg='aView', type='UIView*', help='The view to print the description of.', default='(id)[UIWindow keyWindow]') ]
-
-  def run(self, arguments, options):
-    if options.upwards:
-      view = arguments[0]
-      description = viewHelpers.upwardsRecursiveDescription(view)
-      if description:
-        print description
-      else:
-        print 'Failed to walk view hierarchy. Make sure you pass a view, not any other kind of object or expression.'
-    else:
-      lldb.debugger.HandleCommand('po (id)[' + arguments[0] + ' recursiveDescription]')
-
-
-class FBPrintCoreAnimationTree(fb.FBCommand):
-  def name(self):
-    return 'pca'
-
-  def description(self):
-    return 'Print layer tree from the perspective of the render server.'
-
-  def run(self, arguments, options):
[…]

### 2014-03-17 EasyMerge/tests/chisel/commands/FBVisualizationCommands.py

@@ -1,81 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import lldb
-import os
-import time
-import fblldbbase as fb
-import fblldbobjecthelpers as objectHelpers
-
-def lldbcommands():
-  return [
-    FBVisualizeCommand()
-  ]
-
-def _showImage(commandForImage):
-  commandForImage = '(' + commandForImage + ')'
-  imageDirectory = '/tmp/xcode_debug_images/'
-
-  createDirectoryFormatStr = '[[NSFileManager defaultManager] createDirectoryAtPath:@"{}" withIntermediateDirectories:YES attributes:nil error:NULL]'
-  createDirectoryCMD = createDirectoryFormatStr.format(imageDirectory)
-  lldb.debugger.HandleCommand('expr (void) ' + createDirectoryCMD)
-
-  imageName = time.strftime("%Y-%m-%d-%H-%M-%S", time.gmtime()) + ".png"
-  imagePath = imageDirectory + imageName
-  createImageFormatStr = '[[NSFileManager defaultManager] createFileAtPath:@"{}" contents:(id)UIImagePNGRepresentation({}) attributes:nil]'
-  createImageCMD = createImageFormatStr.format(imagePath, commandForImage)
-
-  lldb.debugger.HandleCommand('expr (void) ' + createImageCMD)
-  os.system('open ' + imagePath)
-
-def _showLayer(layer):
-  layer = '(' + layer + ')'
-
-  lldb.debugger.HandleCommand('expr (void)UIGraphicsBeginImageContextWithOptions(((CGRect)[(id)' + layer + ' bounds]).size, NO, 0.0)')
-  lldb.debugger.HandleCommand('expr (void)[(id)' + layer + ' renderInContext:(void *)UIGraphicsGetCurrentContext()]')
-
-  frame = lldb.debugger.GetSelectedTarget().GetProcess().GetSelectedThread().GetSelectedFrame()
-  result = frame.EvaluateExpression('(UIImage *)UIGraphicsGetImageFromCurrentImageContext()')
-  if result.GetError() is not None and str(result.GetError()) != 'success':
-    print result.GetError()
-  else:
-    image = result.GetValue()
[…]

### 2014-03-17 EasyMerge/tests/chisel/fblldbobjcruntimehelpers.py

@@ -1,75 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import lldb
-import fblldbbase as fb
-import re
-
-def objc_getClass(className):
-  command = '(void*)objc_getClass("{}")'.format(className)
-  value = fb.evaluateExpression(command)
-  return value
-
-def object_getClass(object):
-  command = '(void*)object_getClass({})'.format(object)
-  value = fb.evaluateExpression(command)
-  return value
-
-def class_getName(klass):
-  command = '(const char*)class_getName({})'.format(klass)
-  value = fb.evaluateExpressionValue(command).GetSummary().strip('"')
-  return value
-
-def class_getSuperclass(klass):
-  command = '(void*)class_getSuperclass({})'.format(klass)
-  value = fb.evaluateExpression(command)
-  return value
-
-def class_getInstanceMethod(klass, selector):
-  command = '(void*)class_getInstanceMethod({}, @selector({}))'.format(klass, selector)
-  value = fb.evaluateExpression(command)
-  return value
-
-def currentArch():
-  targetTriple = lldb.debugger.GetSelectedTarget().GetTriple()
-  arch = targetTriple.split('-')[0]
-  return arch
-
-def functionPreambleExpressionForSelf():
-  arch = currentArch()
-  expressionForSelf = None
-  if arch == 'i386':
-    expressionForSelf = '*(id*)($esp+4)'
-  elif arch == 'x86_64':
-    expressionForSelf = '(id)$rdi'
-  elif arch == 'arm64':
-    expressionForSelf = '(id)$x0'
-  elif re.match(r'^armv.*$', arch):
-    expressionForSelf = '(id)$r0'
-  return expressionForSelf
-
-def functionPreambleExpressionForObjectParameterAtIndex(parameterIndex):
-  arch = currentArch()
-  expresssion = None
-  if arch == 'i386':
-    expresssion = '*(id*)($esp + ' + str(12 + parameterIndex * 4) + ')'
-  elif arch == 'x86_64':
-    if (parameterIndex > 3):
-      raise Exception("Current implementation can not return object at index greater than 3 for arc x86_64")
-    registersList = ['rdx', 'rcx', 'r8', 'r9']
[…]

### 2014-03-17 EasyMerge/tests/chisel/fblldbviewhelpers.py

@@ -1,86 +1,0 @@
-#!/usr/bin/python
-
-# Copyright (c) 2014, Facebook, Inc.
-# All rights reserved.
-#
-# This source code is licensed under the BSD-style license found in the
-# LICENSE file in the root directory of this source tree. An additional grant
-# of patent rights can be found in the PATENTS file in the same directory.
-
-import lldb
-
-import fblldbbase as fb
-
-def flushCoreAnimationTransaction():
-  lldb.debugger.HandleCommand('expr (void)[CATransaction flush]')
-
-def setViewHidden(object, hidden):
-  lldb.debugger.HandleCommand('expr (void)[' + object + ' setHidden:' + str(int(hidden)) + ']')
-  flushCoreAnimationTransaction()
-
-def maskView(viewOrLayer, color, alpha):
-  unmaskView(viewOrLayer)
-  window = fb.evaluateExpression('(UIWindow *)[[UIApplication sharedApplication] keyWindow]')
-  origin = convertPoint(0, 0, viewOrLayer, window)
-  size = fb.evaluateExpressionValue('(CGSize)((CGRect)[(id)%s frame]).size' % viewOrLayer)
-
-  rectExpr = '(CGRect){{%s, %s}, {%s, %s}}' % (origin.GetChildMemberWithName('x').GetValue(),
-                                               origin.GetChildMemberWithName('y').GetValue(),
-                                               size.GetChildMemberWithName('width').GetValue(),
-                                               size.GetChildMemberWithName('height').GetValue())
-  mask = fb.evaluateExpression('[((UIView *)[UIView alloc]) initWithFrame:%s]' % rectExpr)
-
-  lldb.debugger.HandleCommand('expr (void)[%s setTag:(NSInteger)%s]' % (mask, viewOrLayer))
-  lldb.debugger.HandleCommand('expr (void)[%s setBackgroundColor:[UIColor %sColor]]' % (mask, color))
-  lldb.debugger.HandleCommand('expr (void)[%s setAlpha:(CGFloat)%s]' % (mask, alpha))
-  lldb.debugger.HandleCommand('expr (void)[%s addSubview:%s]' % (window, mask))
-  flushCoreAnimationTransaction()
-
-def unmaskView(viewOrLayer):
-  window = fb.evaluateExpression('(UIWindow *)[[UIApplication sharedApplication] keyWindow]')
[…]

### 2014-03-17 EasyMerge/merger/analyzer.py
updated parameter in analyzer

@@ -4,4 +4,4 @@ import merger
 class Analyzer():
     def analyze(self, path):
         print 'Analyzing ' + path + '...'
-        return merger.main(path, 10)
+        return merger.main(path, 10, 4)

### 2014-03-17 EasyMerge/merger/evaluation.py
final ver 2

@@ -12,7 +12,6 @@ def getTotalSourceLineNumbers(dir):
             files[:] = [f for f in files]
             yield (dirpath, dirs, files)
     def getLineNumber(filename):
-        total_file+=1
         f = open(filename, "r")
         lines = f.readlines()
         return len(lines)
@@ -25,10 +24,9 @@ def getTotalSourceLineNumbers(dir):
             if f[-3:]!=".py":
                 continue
             filename = os.path.join(dirpath, f)
+            total_file+=1
             linenum = getLineNumber(filename)
             total_num += linenum
-    print total_num,"lines in total"
-    print total_file,"files in total"
     return total_num, total_file
 
 
@@ -40,6 +38,8 @@ def getOtherStats(dir, distance_threshold, size_threshold):
         print i
     
 if __name__ == '__main__':
-    dir_name = "../tests/beets"
+    dir_name = "../tests/fig"
     total_num, total_file = getTotalSourceLineNumbers(dir_name)
     getOtherStats(dir_name, 10, 4)
+    print total_num,"lines in total"
+    print total_file,"files in total"

### 2014-03-17 EasyMerge/merger/merger.py

@@ -284,7 +284,7 @@ def main(dir,distance_threshold, size_threshold):
     return mergeResults
 
 if __name__ == '__main__':
-    main("../tests/beets", 10, 4)
+    main("../tests/", 10, 4)
     
     for i in mergeResults:
         i.output()

### 2014-03-17 EasyMerge/merger/clone_refiner.py
final ver 3

@@ -53,6 +53,7 @@ def getInfoFromSet(dSet, pair = False):
         indepLine = {}
         for i in dSet:
             for dup in i: 
+                #print dup
                 srcName = dup.getSourceFile().getFileName()
                 for n in dup.getCoveredLineNumbers():
                     tag = srcName+"@"+str(n)
@@ -317,6 +318,14 @@ def spreadMixSet(dSet, type_list):
     
     for cluster in dSet:
         type = type_list[dSet.index(cluster)]
+        if type=="Def" and len(cluster[0])>1:
+            new_insert = []
+            for i in range(len(cluster[0])):
+                new_set = []
+                for d in cluster:
+                    new_set.append(StatementSequence([d[i]]))
+                new_insert.append(new_set)
+            dSet[dSet.index(cluster)] = new_insert
         if isinstance(type,tuple):
             new_clusters = type[1]
             new_insert = []
@@ -337,6 +346,8 @@ def spreadMixSet(dSet, type_list):
         elif len(cluster)==0:
             dSet = dSet[:i]+dSet[i+1:]
             type_list = type_list[:i]+type_list[i+1:]
+            i-=1
+
         i+=1
         if i>=len(dSet):
             break 

### 2014-03-17 EasyMerge/merger/evaluation.py

@@ -38,7 +38,7 @@ def getOtherStats(dir, distance_threshold, size_threshold):
         print i
     
 if __name__ == '__main__':
-    dir_name = "../tests/fig"
+    dir_name = "../tests/"
     total_num, total_file = getTotalSourceLineNumbers(dir_name)
     getOtherStats(dir_name, 10, 4)
     print total_num,"lines in total"

### 2014-03-17 EasyMerge/merger/merger.py

@@ -25,6 +25,7 @@ stat ={"Merged":0,
        "ErrorDef":0,
        "DiffStmt":0,
        "ErrorStmt":0,
+       "UnknownType":0,
        "DiffPak":0,
        "Reduction":[]}
 
@@ -64,6 +65,36 @@ def tmpDistributor(dSet, dInfo, src_ast_list):
             else:
                 print "Error"
                 #break   
+        elif info[0]=="Def" and info[1]>0:
+            print "Type2"
+            too_short = False
+            for i in range(len(cluster)):
+                seq = cluster[i][0]
+                new_seq = seq.getChilds()[-1]
+                is_ret = new_seq.getChilds()[-1]
+                if is_ret.getName()=="Return":
+                    new_seq = StatementSequence(new_seq.getChilds()[:-1])
+                else:
+                    new_seq = StatementSequence(new_seq.getChilds())
+                
+                if not new_seq or tagging(new_seq)[2] - tagging(new_seq)[1] < 3:
+                    print "TOO SHORT DEF"
+                    too_short = True
+                    stat["DiffDef"]+=1
+                    break                
+                else:
+                    cluster[i] = new_seq
+            if too_short:
+                continue
+                    
+            if processNonIdenticalStmt(src_ast_list, cluster, i):
+                print "Success"
+                stat["Merged"]+=1
+                stat["MergedDiff"]+=1
+                stat["MergedDist"]+=info[1]
+            else:
+                print "Error"
+
         elif info[0]=="Stmt" and info[1]>0:
             print "Type3"
             if processNonIdenticalStmt(src_ast_list, cluster, i):
@@ -74,7 +105,7 @@ def tmpDistributor(dSet, dInfo, src_ast_list):
             else:
                 print "Error"
         else:
-            stat["DiffDef"]+=1
+            stat["UnknownType"]+=1
     
     for m in mergeResults:
         
@@ -89,13 +120,13 @@ def tmpDistributor(dSet, dInfo, src_ast_list):
             oldLines+=lines
         newLines = m.lines+len(m._caller)
         
-        if newLines>oldLines:
+        '''if newLines>oldLines:
             print "New Code:", m.lines
             print "Caller:", len(m._caller)
             old = []
             for i in m._caller:
                 old.append(i[2]-i[1]+1)
-            print "Old Code:", old
+            print "Old Code:", old'''
         
         stat["Reduction"].append(oldLines-newLines)
[…]

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/commands.py
add test

@@ -1,0 +1,115 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+import paste.deploy.config
+import paste.fixture
+from paste.registry import RegistryManager
+from paste.script import command
+from paste.deploy import appconfig        
+from r2.config.environment import load_environment
+from paste.script.pluginlib import find_egg_info_dir
+from pylons.wsgiapp import PylonsApp
+
+from r2.config.middleware import RedditApp
+
+#from pylons.commands import ShellCommand, ControllerCommand, \
+#     RestControllerCommand
+
+import os, sys
+#
+# commands that will be available by running paste with this app
+#
+
+class RunCommand(command.Command):
+    max_args = 2
+    min_args = 1
+
+    usage = "CONFIGFILE CMDFILE.py"
+    summary = "Executed CMDFILE with pylons support"
+    group_name = "Reddit"
+
+
+    parser = command.Command.standard_parser(verbose=True)
+    parser.add_option('-c', '--command',
+                      dest='command',
+                      help="execute command in module")
+    parser.add_option("", "--proctitle",
+                      dest="proctitle",
+                      help="set the title seen by ps and top")
+
+    def command(self):
+        try:
+            if self.options.proctitle:
+                import setproctitle
+                setproctitle.setproctitle("paster " + self.options.proctitle)
+        except ImportError:
+            pass
+
+        here_dir = os.getcwd()
+
+        is_standalone = self.args[0].lower() == 'standalone'
+        if is_standalone:
[…]

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/controllers/captcha.py

@@ -1,0 +1,54 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+from reddit_base import RedditController
+import StringIO
+import r2.lib.captcha as captcha
+from pylons import c, response
+
+from r2.controllers.api_docs import api_doc, api_section
+
+class CaptchaController(RedditController):
+    @api_doc(api_section.captcha, uri='/captcha/{iden}')
+    def GET_captchaimg(self, iden):
+        """
+        Request a CAPTCHA image given an `iden`.
+
+        An iden is given as the `captcha` field with a `BAD_CAPTCHA`
+        error, you should use this endpoint if you get a
+        `BAD_CAPTCHA` error response.
+
+        Responds with a 120x50 `image/png` which should be displayed
+        to the user.
+
+        The user's response to the CAPTCHA should be sent as `captcha`
+        along with your request.
+
+        To request a new CAPTCHA,
+        use [/api/new_captcha](#POST_api_new_captcha).
+        """
+        image = captcha.get_image(iden)
+        f = StringIO.StringIO()
+        image.save(f, "PNG")
+        response.content_type = "image/png;"
+        return f.getvalue()
+    

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/controllers/errorlog.py

@@ -1,0 +1,35 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+from pylons import request, g
+from reddit_base import RedditController
+from r2.lib.pages import AdminPage, AdminErrorLog
+from r2.lib.validator import validate, VAdmin
+
+class ErrorlogController(RedditController):
+    @validate(VAdmin())
+    def GET_index(self):
+        res = AdminPage(content = AdminErrorLog(),
+                        title = 'error log',
+                        show_sidebar = False
+                        ).render()
+        return res

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/models/__init__.py

@@ -1,0 +1,38 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+from account import *
+from link import *
+from listing import *
+from builder import *
+from vote import *
+from report import *
+from subreddit import *
+from flair import *
+from award import *
+from bidding import *
+from mail_queue import Email, has_opted_out, opt_count
+from gold import *
+from admintools import *
+from token import *
+from modaction import *
+from promo import *

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/models/award.py

@@ -1,0 +1,206 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+from r2.lib.db.thing import Thing, Relation, NotFound
+from r2.lib.db.userrel import UserRel
+from r2.lib.db.operators import asc, desc, lower
+from r2.lib.memoize import memoize
+from r2.models import Account
+from pylons import c, g, request
+
+class Award (Thing):
+    _defaults = dict(
+        awardtype = 'regular',
+        api_ok = False
+        )
+
+    @classmethod
+    @memoize('award.all_awards')
+    def _all_awards_cache(cls):
+        return [ a._id for a in Award._query(sort=asc('_date'), limit=100) ]
+
+    @classmethod
+    def _all_awards(cls, _update=False):
+        all = Award._all_awards_cache(_update=_update)
+        # Can't just return Award._byID() results because
+        # the ordering will be lost
+        d = Award._byID(all, data=True)
+        return [ d[id] for id in all ]
+
+    @classmethod
+    def _new(cls, codename, title, awardtype, imgurl, api_ok):
+        a = Award(codename=codename, title=title, awardtype=awardtype,
+                  imgurl=imgurl, api_ok=api_ok)
+        a._commit()
+        Award._all_awards_cache(_update=True)
+
+    @classmethod
+    def _by_codename(cls, codename):
+        q = cls._query(lower(Award.c.codename) == codename.lower())
+        q._limit = 1
+        award = list(q)
+
+        if award:
[…]

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/models/token.py

@@ -1,0 +1,718 @@
+# The contents of this file are subject to the Common Public Attribution
+# License Version 1.0. (the "License"); you may not use this file except in
+# compliance with the License. You may obtain a copy of the License at
+# http://code.reddit.com/LICENSE. The License is based on the Mozilla Public
+# License Version 1.1, but Sections 14 and 15 have been added to cover use of
+# software over a computer network and provide for limited attribution for the
+# Original Developer. In addition, Exhibit A has been modified to be consistent
+# with Exhibit B.
+#
+# Software distributed under the License is distributed on an "AS IS" basis,
+# WITHOUT WARRANTY OF ANY KIND, either express or implied. See the License for
+# the specific language governing rights and limitations under the License.
+#
+# The Original Code is reddit.
+#
+# The Original Developer is the Initial Developer.  The Initial Developer of
+# the Original Code is reddit Inc.
+#
+# All portions of the code written by reddit are Copyright (c) 2006-2013 reddit
+# Inc. All Rights Reserved.
+###############################################################################
+
+import datetime
+import functools
+from os import urandom
+from base64 import urlsafe_b64encode
+
+from pycassa.system_manager import ASCII_TYPE, DATE_TYPE, UTF8_TYPE
+
+from pylons import g, c
+from pylons.i18n import _
+
+from r2.lib.db import tdb_cassandra
+from r2.lib.db.thing import NotFound
+from r2.models.account import Account
+
+def generate_token(size):
+    return urlsafe_b64encode(urandom(size)).rstrip("=")
+
+
+class Token(tdb_cassandra.Thing):
+    """A unique randomly-generated token used for authentication."""
+
+    _extra_schema_creation_args = dict(
+        key_validation_class=ASCII_TYPE,
+        default_validation_class=UTF8_TYPE,
+        column_validation_classes=dict(
+            date=DATE_TYPE,
+            used=ASCII_TYPE
+        )
+    )
+
+    @classmethod
+    def _new(cls, **kwargs):
+        if "_id" not in kwargs:
+            kwargs["_id"] = cls._generate_unique_token()
+
+        token = cls(**kwargs)
+        token._commit()
+        return token
+
+    @classmethod
+    def _generate_unique_token(cls):
+        for i in range(3):
+            token = generate_token(cls.token_size)
+            try:
+                cls._byID(token)
+            except tdb_cassandra.NotFound:
+                return token
+            else:
+                continue
+        raise ValueError
+
[…]

### 2014-03-18 EasyMerge/tests/reddit/r2/r2/public/static/js/utils.js

@@ -1,0 +1,153 @@
+r.utils = {
+    clamp: function(val, min, max) {
+        return Math.max(min, Math.min(max, val))
+    },
+
+    staticURL: function (item) {
+        return r.config.static_root + '/' + item
+    },
+
+    s3HTTPS: function(url) {
+        if (location.protocol == 'https:') {
+            return url.replace('http://', 'https://s3.amazonaws.com/')
+        } else {
+            return url
+        }
+    },
+
+    joinURLs: function(/* arguments */) {
+        return _.map(arguments, function(url, idx) {
+            if (idx > 0 && url && url[0] != '/') {
+                url = '/' + url
+            }
+            return url
+        }).join('')
+    },
+
+    tup: function(list) {
+        if (!_.isArray(list)) {
+            list = [list]
+        }
+        return list
+    },
+
+    querySelectorFromEl: function(targetEl, selector) {
+        return $(targetEl).parents().andSelf()
+            .filter(selector || '*')
+            .map(function(idx, el) {
+                var parts = [],
+                    $el = $(el),
+                    elFullname = $el.data('fullname'),
+                    elId = $el.attr('id'),
+                    elClass = $el.attr('class')
+
+                parts.push(el.nodeName.toLowerCase())
+
+                if (elFullname) {
+                    parts.push('[data-fullname="' + elFullname + '"]')
+                } else {
+                    if (elId) {
+                        parts.push('#' + elId)
+                    } else if (elClass) {
+                        parts.push('.' + _.compact(elClass.split(/\s+/)).join('.'))
+                    }
+                }
+
+                return parts.join('')
+            })
+            .toArray().join(' ')
+    },
+
+    serializeForm: function(form) {
+        var params = {}
+        $.each(form.serializeArray(), function(index, value) {
+            params[value.name] = value.value
+        })
+        return params
+    },
+
+    _pyStrFormatRe: /%\((\w+)\)s/g,
+    pyStrFormat: function(format, params) {
+        return format.replace(this._pyStrFormatRe, function(match, fieldName) {
+            if (!(fieldName in params)) {
+                throw 'missing format parameter'
+            }
+            return params[fieldName]
+        })
+    },
+
+    _mdLinkRe: /\[(.*?)\]\((.*?)\)/g,
+    formatMarkdownLinks: function(str) {
+        return _.escape(str).replace(this._mdLinkRe, function(match, text, url) {
[…]

### 2014-03-18 paper/paper.tex
update paper

@@
 The first step of EasyMerge is to run CloneDigger at target source tree, take its output and format and standardize it for our own usage.
-The core of this step is to classify code clones and get the ones that we not only can but also want to merge.
+The core of this step is to classify code clones and get the ones that we not only can but also want to merge. Although CloneDigger takes
+a dozen configuration parameters, we use most of them as defaults. For our preprocessing, we only override {\bf distance-threshold} and {\bf size-threshold}
+to {\bf 10} and {\bf 4} for we are only interested in clone segments of no more than 10 anti-unification distance from each other and no less than 4 lines in length.
+
+Additionally, we put identical clone pairs into sets. For example, if we have three pairs of [A, B], [B, C], [C, A] from CloneDigger's output, we generate a clone set
+of [A, B, C] instead for our following merging stage. As not all clone sets can be handled by our algorithm, we also implement a filter to remove all unrefactorable
+clones before entering next step.
+
+\subsection{Recommendation Evaluation}
+Although EasyMerge can handle multiple types of code clones, not all of them shall be recommended. As a matter of fact, we use a combination of 
+package path analyzer and weighted evaluation formula to make our recommendation decisions.
 
@@
 and ``Wagtail - a new Django content management system".
+
+\section{Conclusion and Future Work}
+Code clones are very common in medium to large scale software applications.
+Detecting and refactoring unnecessary clones can help us provide cleaner, easier to understand, and readily reusable code.
+However, there are many different types of clones and many subtle implications while dealing with them when coupling and
+inheritance is involved. Our proposed solution, EasyMerge, is a clone refactoring tool based on anti-unification clone detector 
+CloneDigger, that can handle most Type-1 clones and many Type-2 clones. It fixes external variable and function reference
+and provide merge recommendation based on evaluation of externality and package information analysis.
 

### 2014-03-18 paper/paper.tex
paper updates

@@
 and provide merge recommendation based on evaluation of externality and package information analysis.
+Moreover, EasyMerge guarantees the consistency of functionality before and after code merging.
+
+However, EasyMerge still has limitations. First of all, not all code clones can be detected by CloneDigger or any existing
+code clone detection approach in general. For future work, we may upgrade EasyMerge's clone detection engine to locate
+more clones in code base.
+
+Secondly,
 

### 2014-03-18 paper/paper.tex
al

@@
 128 KB L1 cache, 6 MB L2 cache (1 MB per core), and 8 MB shared L3 cache. The machine runs Ubuntu Desktop 12.04, Python
-2.7.5 and has all related packages installed. For test cases, we have three popular Python powered open source projects found on GitHub of different sizes and covers
+2.7.5 and has all related packages installed.
+For test cases, we have two sets of open source projects written in Python. The first set contains 5 most famous projects on GitHub:
+\begin{enumerate}
+\item Tornado - A Python web framework and asynchronous networking library
+\item Redis Python Client - Client for the most famous in-memory database that persists on disk
+\item Reddit - The code that powers reddit.com
+\item Scrapy - A fast high-level screen scraping and web crawling framework for Python.
+\item PyMongo - The Python driver for MongoDB
+\end{enumerate}
+
+The second set has 6 randomly selected projects from GitHub:
+\begin{enumerate}
+\item PyStruct - Simple structured learning framework for Python
+\item YouTube-dl - Small command-line program to download videos from YouTube.com and other video sites
+\item Tweepy - An easy-to-use Python library for accessing the Twitter API
+\item Beets - The media library management system for obsessive-compulsive music geeks
+\item Fig - Fast, isolated development environments using Docker
+\item Wagtail - A new Django content management system
+\end{enumerate}
+
+three popular Python powered open source projects found on GitHub of different sizes and covers
 different usage domains.
@@
 code clone detection approach in general. For future work, we may upgrade EasyMerge's clone detection engine to locate
-more clones in code base.
+more clones in code base. Secondly, we can add support to merge more Type-2 and Type-3 clones (there is no reliable detection of Type-4 clones at the moment yet).
+It's very challenging to merge Type-3 clones as we may need to add context-based analysis to sort out extra statements and different layouts of similar code.
 
-Secondly,
+Furthermore,
 

### 2014-03-18 paper/paper.tex
paper updates

@@
 
-three popular Python powered open source projects found on GitHub of different sizes and covers
-different usage domains.
-They are ``Beets - the media library management system for obsessive-compulsive music geeks", ``Fig - fast, isolated development environments using Docker",
-and ``Wagtail - a new Django content management system".
+We predict the most famous ones should be better written and contain less code clones in average and we will see if the results stick to our prediction.
 
@@
 
-Furthermore,
+Furthermore, the current version of EasyMerge cannot merge similar classes and all duplicated classes are filtered out in preprocessing.
+In the future, we can add mechanism to merge similar classes, automatically generate parent classes and extract similar members and methods to the parents.
+Additionally, current mergeable clones are within code blocks (at the same indentation level for Python). We are also interested in merging code clones that cross
+multiple levels and scopes. We may break big clone fragments into smaller pieces and merge accordingly.
 

### 2014-03-19 paper/paper.tex
lala finished

@@
 Once the scanning phase is completed, a list of refactorable clone sets are displayed in the ``Possible Merges" box at top left.
-All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record.
+All items in the list are initially coloured green, once a merge is done, the colour will be changed to red for the record. Moreover,
+the items in the list are ranked based on our recommendation evaluation from high to low.
 
@@
 to {\bf 10} and {\bf 4} for we are only interested in clone segments of no more than 10 anti-unification distance from each other and no less than 4 lines in length.
+On top of that, distance must be no more than code length as we don't want more than one difference at a line of code.
 
-Additionally, we put identical clone pairs into sets. For example, if we have three pairs of [A, B], [B, C], [C, A] from CloneDigger's output, we generate a clone set
-of [A, B, C] instead for our following merging stage. As not all clone sets can be handled by our algorithm, we also implement a filter to remove all unrefactorable
-clones before entering next step.
+Secondly, we strip off non logical but required lines such as imports and definitions. For a code block of statements, if the last line is only a returning clause, we
+modify the clone fragment by removing the returning line and keeping the rest. After text-based manipulation, we cluster all clone pairs and put them into sets
+based on similarity. For example, if we have three pairs of [A, B], [B, C], [C, A] from CloneDigger's output, we generate a clone set
+of [A, B, C] instead for our following merging stage.
+
+Next, we look for overlapping code fragments in clones, to make our lives easier, for each set of overlapping clones, we only keep the longer part of the overlapping fragments
+and ignore the shorter ones. For a code fragment of ABCDEFG where each letter is of the same code length, if BCD and CDEF are both duplicate code in different sets,
+as they are overlapping each other,
+we remove the set containing BCD and only try to merge the set with CDEF.
+
+Additionally, if we have a set containing clone fragments which consist of both statements and function definitions, we separate and break them into multiple individual sets and guarantee that for any clone set, it either only have duplicated statements or function definition, as it's very difficult to merge multi-purpose code blocks.
+For example, if we have a set of clone fragments of AFB where block A and B are statements only and F is a function definition, we will break it into three sets which
+contain only A, F, and B accordingly.
+
+Note: if you have files in the source tree that you do not want to perform analysis or merge of any kind, you need to manually exclude them from the selected folder.
+
+\subsection{Clone Classification}
+After preprocessing, we classify clone sets into multiple types as we are handling each type independently in the merging process. Firstly,
+we call the anti-unifier in CloneDigger to obtain the anti-unification distance between code fragments in each clone set to determine if they
+are Type-1 or Type-2 clones. Then, we check if the clone fragments in one set are in the same Python file or scattered across multiple files (this is the most common case).
+Moreover, we separate duplicated functions and statements in this step as they are handled differently when extracting methods in the merging phase.
+
+\subsection{Merging}
+We first prepare merging by examine the Abstract Syntax Tree(AST) for each code clone fragment to extract some deeper information: (1) all ``import" information
+(2) all class definitions and their associated scopes (3) all function calls and the scopes these calls reside.
+
+Then we deal with statement clones and function clones separately. For functions, we create a helper function with all code extracted from the function body.
+Then we scan the code base and locate all reference calls to the original functions in the clone set and replace them with calls to the newly generated helper function.
+For blocks containing only statements, similarly, we extract the code and create a helper function to host the code. And the original code blocks are replaced by
+function calls to the newly generated helper function. If the clones in a set are all from the same file, we place the helper function to the same file. If they are 
+from different files, we parse package dependency and find the last shared package and put the helper function there to make sure scopes are maintained properly.
+Moreover, we ensure unique function name will be provided for helper functions and user can also override it in EasyMerge.
+
+For the actual merging phase and the generation of the helper functions, 
+we start with creating a potential helper function copy for each fragment in a clone set. 
+We first scan for all variables, function calls and objects. Then we try to match them in 
+deeper information collected before. For lines containing items that can be used without external reference, we move them directly to the copy. For everything else,
+we put them into a function signature line as input parameters so we are able to use them in the future function body. 
+We then look for variables and objects references to items in the 
+source files happen after the clone fragment in the same scope. For any occurrence of such items, we add them to a returning line so they can still be referred to 
+later in the original source files. Then we append the signature line and returning line to the helper function copy.
+
+Last but not least, we compare each newly generated helper function copy from each fragment, if they are all identical, we use one copy as the actual extracted helper function
+and write the changes to files. If not, we check if they are Type-1 clones. For Type-1 clones, we merge their individual signature line and returning line and
+replace the corresponding line in the helper function copy before creating the real helper function. For non Type-1 clones, if the differences are only about constants,
+we merge by replacing all constants with variables and pass them as input parameters in helper function's signature and update calls to the helper function in code base accordingly.
+For other non Type-1 clones, we perform an AST pattern matching and analyzing their
+symbol table and try to merge clones have same pattern of variable/function call/object referencing sequence. For a clone set of two fragments, if they both access variables
+with similar patterns of a, b, a, c and e, f, e, g, then we can group [a, e], [b, f], [c, g] and treat them as three special variables in the generated helper and update
+the function signature and returning line accordingly. In contrast, patterns of a, b, a, c and a, b, b, d cannot be merged. And we ignore all other clones not covered above
+as they cannot be handled by EasyMerge yet.
 
@@
 Although EasyMerge can handle multiple types of code clones, not all of them shall be recommended. As a matter of fact, we use a combination of 
-package path analyzer and weighted evaluation formula to make our recommendation decisions.
+package path analyzer and weighted evaluation formula to make our recommendation decisions. Generally speaking, we may not want to merge code
+in separate libraries/packages so that we do not introduce extra coupling and each library may be used independently. 
+Moreover, too many external references that pass parameters around may also be misleading and against our will to simplify code bases.
+As a result, the recommendation evaluation formula is defined as following:
+\begin{displaymath}
+f(RE) = w_{1} * l - w_{2} * e - w_{3} * r - w_{4} * d
+\end{displaymath}
+where $w_{1}$, $w_{2}$, $w_{3}$, $w_{4}$ are weights,  $l$ is the number of duplicate lines, $e$ is number of external reference (including variables, functions, and objects),
+$r$ is number of packed extra return values. Additionally, $d$ is the package difference defined as the the minimum package difference length in a clone set.
+For example, if we have a set of two files a.b.c and a.b.d.e, the package difference length is 1 and 2 respectively as they differ after package b. And thus the $d$ value is
+$min(1, 2) = 1$.
+
+For now, we did some testing and are setting the weights at 
+$w_{1} = 0.5$, $w_{2} = 1$, $w_{3} = 2$, $w_{4} = 2$ as we don't want too much externality with too few lines of code. And extra return values are more confusing than
+extra input parameters. To help user make the decision, we recommend a merge if $f(RE) > 8$, somewhat recommend a merge if $ 0 \le f(RE) \le 8$, and let user merge
+with cautions when $f(RE) < 0$.
+It give us modest reasonable behaviour we want after some manual analysis of each clone set.
+In the future, we are interested to perform a actual survey with real software developers to reconfigure these weights to better fit our purpose.
 
@@
 For test cases, we have two sets of open source projects written in Python. The first set contains 5 most famous projects on GitHub:
-\begin{enumerate}
+\begin{itemize}
 \item Tornado - A Python web framework and asynchronous networking library
@@
 \item PyMongo - The Python driver for MongoDB
-\end{enumerate}
+\end{itemize}
 
 The second set has 6 randomly selected projects from GitHub:
-\begin{enumerate}
+\begin{itemize}
 \item PyStruct - Simple structured learning framework for Python
@@
 \item Wagtail - A new Django content management system
-\end{enumerate}
+\end{itemize}
 
 We predict the most famous ones should be better written and contain less code clones in average and we will see if the results stick to our prediction.
+
+\begin{figure}
+\centering
+\epsfig{file=result1.pdf}
+\caption{Preprocessing Results}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=result3.pdf}
+\caption{Classification Results}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=result2.pdf}
+\caption{Mergeability Analysis}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=result4.pdf}
+\caption{Merging Results}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=result5.pdf}
+\caption{Recommendation Evaluation Distribution}
+\end{figure}
+
+\subsection{Preprocessing Results}
+This test data in {\bf Figure 2.} shows number of lines, clone sets, set size, duplicate lines (lines in clone sets / total number of lines), and repeated lines for
+both test sets after each filtering steps. As shown in the table, we removed many double counted clones. After all preprocessing steps, we have 9.67\% and
+4.26\% duplicate lines left that we are able to merge, respectively, which is more than half of the code clones provided by CloneDigger. Set size was 2 before clustering
+as set were pairs before the clustering step.
+
+\subsection{Classification}
+Classification test data in {\bf Figure 3.} shows how we classify clones into different types to handle them accordingly.
+Statements and Functions data is very volatile as it somewhat depends on developers personal coding style.
+Identical and Different data shows majority of clones we are merging are not Type-1, which correlates to our prediction
+before the experiments as developers hardly actually copy and paste exact code. Same Files and Different Files shows that
+it's slightly more common to have clone code residing in the same files, although we couldn't really reason about this observation.
+
+\subsection{Mergeability Analysis}
+{\bf Figure 4.} shows what percentage of code clones we can merge out of the ones provided by CloneDigger, and the distribution of clones 
+we cannot handle according to different reasons:
+\begin{itemize}
+\item Reason 1: Type-3 clones - we are unable to merge any Type-3 clones at this moment
+\item Reason 2: Clone Fragments of length which is too short. We don't want to merge these clones as it's not improving readability at all
+\item Reason 3: Merges that throw unexpected exceptions for some reason that cannot pass our sanity check
+\end{itemize}
+We can merge almost all Type-1 clones and more than half of Type-2 clones. For clones that we cannot merge, most of them are Type-3 clones.
+
+\subsection{Merging Results}
+{\bf Figure 5.} shows the overall merging results. The data for random selected projects is more interesting as it is more practical for our
+everyday software projects. The data is for merging all mergeable clones without considering any recommendation information. 
+We can merge about 3.51\% code in total which is not a bad result, but each individual merge will only remove 9.21 lines of code in average
+which is not very ideal but reasonable as it includes many not recommended merges of smaller line counts. Distance and external references
+results tell that it's very common to have Type-2 clones and externality in code fragments. Note that external references value here include both
+variable/function/objects references and returned variables for future reference. It shows we are rarely able to perform simple merges and need
+to fix reference errors here and there.
+
+\subsection{Recommendation Evaluation}
+{\bf Figure 6.} is the distribution graph of our recommendation evaluation formula $f(RE)$. As we can see from the graph, about 45\% clones
+are categorized as somewhat recommended to merge, while 40\% are not recommended with a below zero evaluation. And only around 15\% clones
+are recommended. Which makes sense to us as we are only confident enough to merge clones that saves a lot of lines and do not introduce too much
+extra complexity, and which only occupy a relatively small portion of all clones detected by CloneDigger. And we do want developers to actually
+think about and make the merging decision carefully.
+
+\subsection{Random Selected VS Famous Projects}
+When comparing the results for our random selected projects and most famous projects from GitHub, the difference is quite noticeable.
+Firstly, there are way less (almost half) duplicate lines in famous projects. Secondly, famous projects also have less set size which corresponds to
+duplicate code across multiple fragments. Thirdly, for famous projects, most clone sets consist fragments inside same files, which means it has less 
+``copy and paste" from file to file. Additionally, for all clone types detected in famous project, there are more Type-3 clones. In another word,
+there are no simple clones for such famous projects, all occurrences of clones contain quite a few changes and semantics difference.
+Lastly, based on more occurrence of Reason 2 unmergeable clones and lines reduction per set, clones in famous project are way smaller thus
+less are actually clones which are meaningful to merge. The comparison result confirms our prediction that famous open source project are written
+with better care and better refactored compared to random selected projects as they are backed by more professional developers and maintained by
+bigger communities. We do not have access to any medium to large scale commercial propriety software project but we could assume they should
+contain more clones and a higher percentage of those clones shall be merged as for such products delivery time may be more important than
+code quality.
+
+\subsection{Performance}
+Performance-wise, as everything in our program works under O(n) time complexity, time to perform any kind of actions in EasyMerge is insignificant 
+compared to CloneDigger which uses an algorithm of higher order. In fact, user will experience no delay whatsoever after the preprocessing step involving
+CloneDigger is complete.
 
@@
 multiple levels and scopes. We may break big clone fragments into smaller pieces and merge accordingly.
+At the end, we couldn't implement mechanism in this version to detect intentionally introduced clones such as ones in test suites, which could 
+also be a very good research direction for future work.
 

### 2014-03-19 EasyMerge/ui/background.py

@@ -11,7 +11,7 @@ class Background(QtGui.QWidget):
         super(Background, self).__init__()
         self._list = QtGui.QListWidget(self)
         self._tabs = QtGui.QTabWidget(self)
-        self._result = QtGui.QTextBrowser(self)
+        self._result = QtGui.QTextEdit(self)
         self._log = QtGui.QTextBrowser(self)
         self._eval = QtGui.QTextBrowser(self)
         self._merge = QtGui.QPushButton('Merge', self)
@@ -140,7 +140,7 @@ class Background(QtGui.QWidget):
             counter += 1
 
     def generateText(self, title, start, end, replacement):
-        browser = QtGui.QTextBrowser(self)
+        browser = QtGui.QTextEdit(self)
         f = open(title)
         lines = f.readlines()
         f.close()
@@ -158,13 +158,13 @@ class Background(QtGui.QWidget):
                 browser.insertHtml('###REMOVE CODE ABOVE###')
                 browser.insertPlainText('\n')
                 browser.insertPlainText('###REPLACE WITH###')
-                browser.insertPlainText('\n')    
+                browser.insertPlainText('\n')
                 browser.insertPlainText(replacement)
                 browser.insertPlainText('###REPLACE END###')
                 browser.insertPlainText('\n')
             #this actually print the line
             browser.insertPlainText(indent + line)
-            
+
             counter += 1
 
         block = browser.document().findBlockByLineNumber(start + 10)
